### 2025-04-27 paper.tex
add paper and codes

\documentclass{article}

\newcommand{\keywords}[1]{\par\noindent\textbf{Keywords:} #1}
% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{arrows.meta}
% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\SetKw{KwDownTo}{down to}

\title{simple cache-sentive skip list}
\author{Yuchang Ke \\
 \texttt{aceking.ke@gmail.com}
\and Bill Lv \\
\texttt{ideaalloc@gmail.com}
\and Weijie Zhang\\
\texttt{zhangweijie@gmail.com}}

\begin{document}
\maketitle

\begin{abstract}
      We present a cache-sensitive skiplist that is very simple and easy to implement. It only requires a few small modifications to the original skiplist to adapt it to modern CPU architectures, resulting in a performance improvement of 1.2~1.6 times, in some system it can reach 2X or 3X.
      Unlike other optimizations, it does not require specialized instructions such as SIMD or multi-threaded programming. Instead, it takes advantage of modern compiler optimizations, making it more universal. This design can be used not only in in-memory databases or key-value stores, but also in embedded systems.

\keywords{skiplist; cache-sensitive; index structure}
\end{abstract}

\section{Introduction}

In the field of computer science, ordered data structures are a fundamental tool for organizing and managing data. Efficient execution of search, delete, and insert operations is crucial for a wide range of applications, as it directly impacts overall system performance.
To achieve high performance in ordered data structures, many methods have been developed, such as AVL trees and Red-Black trees. However, these structures are relatively complex due to the need for rebalancing. This changed when William Pugh introduced the skip list in 1990\cite{ref1}. It introduced a randomized data structure that simplified implementation compared to traditional balanced trees.

Thanks to its simplicity, the skip list has been adopted by various systems, including databases such as LevelDB\cite{ref2}, Redis\cite{ref7}, and RocksDB\cite{ref3}, Hbase\cite{ref4} in-memory caches, and the inverted index in Lucene.

Skip list can be divided into multiple levels, one data level and multiple index levels. Data level is the lowest level(level 0), which stores all the data nodes. And the index levels provide short paths to access the data node at the data level, and all the levels are linked lists. Because of this, these data nodes and index nodes are non-contiguous in memory address. This causes the performance to be degraded by cache misses.
Although ESL, CSSL has developed cache sensitive skip lists to fit modern CPU architecture, these algorithms are still complex, and CSSL uses SIMD instructions which are special in Intel. We strongly believe that the value of a skiplist lies in its simplicity.  Excessively complex cache-sensitive designs reduce the appeal of skip list variations.

With the emergence of new technologies and computing architectures, particularly multi-core CPUs and vectorization, novel variants of skip lists have been developed. Such as Cache-Sensitive Skiplist (CSSL)\cite{ref5}, which merges nodes at the index level into a single array, which are named fast lanes, and all nodes in the fast lane are sorted. This design is more cache-friendly. It also uses SIMD instructions, ESL( A High-Performance Skiplist with Express Lane\cite{ref6})  also merges the nodes in index levels into a single array, and they use version-based lock protocol and lock-free operation log to implement concurrency.

\section{Design overview}

In this paper, we present a simple and easy-to-implement cache-sensitive skip list. At the data level, it introduces a vector, and the nodes at this level now store arrays instead of single values. Leveraging CPU cache benefits for small arrays to enhance skip list performance. For example, consider a skip list with a vector at the data level; let's suppose the vector's maximum size is 2, as shown in Figure 1.

There are 3 key points: 1) At the data level, we use a sorted array with a fixed maximum length. Since the keys are integers, we choose a maximum length of 128 or less. 2) For all index levels, we use only the first element of the array as a pivot for comparison. 3) The last element of the array is considered solely during insertion operations, and only under particular conditions.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{skiplist.png}
\caption{A simple cache-sensitive skip list}
\label{fig:fig1}
\end{figure}
Our key contributions include: 1. Introducing a vector, which maintains the algorithm's complexity while improving CPU cache hit rate due to its contiguous storage. 2. Reducing the skiplist's level count and pointer overhead by incorporating a vector. 3. Presenting vector-based insertion, search, and deletion algorithms for data nodes, offering a novel perspective for database index design.

\section{Algorithm}
This section gives the algorithm for search, insertion, and deletion. The insertion operation inserts new specified data into the data structure, and the search operation finds data and returns it. The deletion operation deletes data.

In SCSSL, at the data level, data is stored in a single array with a fixed maximum size. As the same as the standard skip list, the level of the node is chosen randomly when the node is created. And a level i node has the same number of forward pointers (also i), the maximum of levels is a constant MaxLevel. It also has a header that leads the search of the data structure, and the last nodes of all levels’ forward pointers point to NIL.

\begin{figure}[ht]
      \centering
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,302); %set diagram left start at 0, and has height of 302

%Shape: Rectangle [id:dp802121456728152] 
\draw   (57.79,105.64) -- (118.41,105.64) -- (118.41,130.32) -- (57.79,130.32) -- cycle ;
%Shape: Rectangle [id:dp9825705095547612] 
\draw   (332.28,103.17) -- (392.89,103.17) -- (392.89,127.86) -- (332.28,127.86) -- cycle ;
%Shape: Rectangle [id:dp248949237262718] 
\draw   (246.56,103.79) -- (307.17,103.79) -- (307.17,128.47) -- (246.56,128.47) -- cycle ;
%Shape: Rectangle [id:dp1628354408576529] 
\draw   (153.04,104.41) -- (213.65,104.41) -- (213.65,129.09) -- (153.04,129.09) -- cycle ;
%Shape: Rectangle [id:dp000018829587681290505] 
\draw   (57.79,56.27) -- (118.41,56.27) -- (118.41,80.96) -- (57.79,80.96) -- cycle ;
%Shape: Rectangle [id:dp247562625981687] 
\draw   (57.79,80.96) -- (118.41,80.96) -- (118.41,105.64) -- (57.79,105.64) -- cycle ;
%Shape: Rectangle [id:dp2644216550992282] 
\draw   (540.96,104.41) -- (601.57,104.41) -- (601.57,129.09) -- (540.96,129.09) -- cycle ;
%Shape: Rectangle [id:dp8347359895416517] 
\draw   (540.96,55.04) -- (601.57,55.04) -- (601.57,79.72) -- (540.96,79.72) -- cycle ;
%Shape: Rectangle [id:dp6823901202027933] 
\draw   (540.96,79.72) -- (601.57,79.72) -- (601.57,104.41) -- (540.96,104.41) -- cycle ;
%Shape: Rectangle [id:dp379773497534003] 
\draw   (153.04,79.72) -- (213.65,79.72) -- (213.65,104.41) -- (153.04,104.41) -- cycle ;
%Shape: Rectangle [id:dp8262463980956687] 
\draw   (153.04,55.04) -- (213.65,55.04) -- (213.65,79.72) -- (153.04,79.72) -- cycle ;
%Shape: Rectangle [id:dp618442800182132] 
\draw   (454.37,103.17) -- (514.98,103.17) -- (514.98,127.86) -- (454.37,127.86) -- cycle ;
%Straight Lines [id:da18234761053431092] 
\draw    (118.41,119.22) -- (151.04,119.22) ;
\draw [shift={(153.04,119.22)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da17691354593928432] 
\draw    (213.65,117.98) -- (246.29,117.98) ;
\draw [shift={(248.29,117.98)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da06545360607750506] 
\draw    (306.3,116.13) -- (332.01,116.13) ;
\draw [shift={(334.01,116.13)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da8917793267177494] 
\draw    (392.89,116.75) -- (452.37,117.34) ;
\draw [shift={(454.37,117.36)}, rotate = 180.58] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da6270688079351094] 
\draw    (514.98,116.13) -- (538.96,116.7) ;
\draw [shift={(540.96,116.75)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da16483082426708995] 
\draw    (119.27,93.91) -- (151.91,93.91) ;
\draw [shift={(153.91,93.91)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Rectangle [id:dp8280971824764716] 
\draw   (332.28,78.49) -- (392.89,78.49) -- (392.89,103.17) -- (332.28,103.17) -- cycle ;
%Straight Lines [id:da6251582090553987] 
\draw    (119.27,69.23) -- (151.91,69.23) ;
\draw [shift={(153.91,69.23)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da906622887317923] 
\draw    (214.52,67.38) -- (536.36,67.38) ;
\draw [shift={(538.36,67.38)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da1247883464855224] 
\draw    (214.52,91.45) -- (330.28,92.05) ;
\draw [shift={(332.28,92.06)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5312111106538793] 
\draw    (392.03,91.45) -- (538.96,91.45) ;
\draw [shift={(540.96,91.45)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Curve Lines [id:da7690346774156931] 
\draw    (107.15,66.76) .. controls (141.78,48.25) and (163.43,87.74) .. (198.07,69.23) ;
%Curve Lines [id:da09969258339888487] 
\draw    (198.07,69.23) .. controls (232.7,50.72) and (171.22,109.34) .. (205.86,90.83) ;
%Curve Lines [id:da17301735066569246] 
\draw    (205.86,90.83) .. controls (240.5,72.32) and (331.41,113.66) .. (366.05,95.15) ;
%Curve Lines [id:da04935924618461396] 
\draw    (361.72,97) .. controls (396.36,78.49) and (358.26,135.26) .. (392.89,116.75) ;
%Curve Lines [id:da43861108104506963] 
\draw    (52.6,38.99) .. controls (87.23,20.48) and (72.51,85.27) .. (107.15,66.76) ;
%Shape: Ellipse [id:dp551323556779669] 
\draw   (410.21,92.06) .. controls (410.21,69.57) and (417.19,51.33) .. (425.8,51.33) .. controls (434.4,51.33) and (441.38,69.57) .. (441.38,92.06) .. controls (441.38,114.56) and (434.4,132.79) .. (425.8,132.79) .. controls (417.19,132.79) and (410.21,114.56) .. (410.21,92.06) -- cycle ;
%Straight Lines [id:da9115207752269137] 
\draw    (445.71,32.82) -- (427.26,49.97) ;
\draw [shift={(425.8,51.33)}, rotate = 317.09] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Rectangle [id:dp44944938443713855] 
\draw   (62.12,221.87) -- (122.73,221.87) -- (122.73,246.55) -- (62.12,246.55) -- cycle ;
%Shape: Rectangle [id:dp8751335667917544] 
\draw   (336.61,219.4) -- (397.22,219.4) -- (397.22,244.08) -- (336.61,244.08) -- cycle ;
%Shape: Rectangle [id:dp2257346710215089] 
\draw   (250.89,220.01) -- (311.5,220.01) -- (311.5,244.7) -- (250.89,244.7) -- cycle ;
%Shape: Rectangle [id:dp8771184949651254] 
\draw   (157.37,220.63) -- (217.98,220.63) -- (217.98,245.32) -- (157.37,245.32) -- cycle ;
%Shape: Rectangle [id:dp5789469841235695] 
\draw   (62.12,172.5) -- (122.73,172.5) -- (122.73,197.18) -- (62.12,197.18) -- cycle ;
%Shape: Rectangle [id:dp5624687649592586] 
\draw   (62.12,197.18) -- (122.73,197.18) -- (122.73,221.87) -- (62.12,221.87) -- cycle ;
%Shape: Rectangle [id:dp13120546674792055] 
\draw   (583.39,220.63) -- (644,220.63) -- (644,245.32) -- (583.39,245.32) -- cycle ;
%Shape: Rectangle [id:dp18910975661576046] 
\draw   (583.39,171.26) -- (644,171.26) -- (644,195.95) -- (583.39,195.95) -- cycle ;
%Shape: Rectangle [id:dp968839873549274] 
\draw   (583.39,195.95) -- (644,195.95) -- (644,220.63) -- (583.39,220.63) -- cycle ;
%Shape: Rectangle [id:dp5100738159249718] 
\draw   (157.37,195.95) -- (217.98,195.95) -- (217.98,220.63) -- (157.37,220.63) -- cycle ;
%Shape: Rectangle [id:dp5130816669129519] 
\draw   (157.37,171.26) -- (217.98,171.26) -- (217.98,195.95) -- (157.37,195.95) -- cycle ;
%Shape: Rectangle [id:dp10069788621732956] 
\draw   (495.07,219.4) -- (555.68,219.4) -- (555.68,244.08) -- (495.07,244.08) -- cycle ;
%Straight Lines [id:da7506949131852723] 
\draw    (122.73,235.44) -- (155.37,235.44) ;
\draw [shift={(157.37,235.44)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5055411274108006] 
\draw    (217.98,234.21) -- (250.62,234.21) ;
\draw [shift={(252.62,234.21)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da7559298876477776] 
\draw    (310.63,232.36) -- (336.34,232.36) ;
\draw [shift={(338.34,232.36)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da08581070094109111] 
\draw    (397.22,232.97) -- (414.27,233.62) ;
\draw [shift={(416.27,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5858905620692174] 
\draw    (557.41,232.36) -- (581.39,232.93) ;
\draw [shift={(583.39,232.97)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da32674036346427937] 
\draw    (123.6,210.14) -- (156.24,210.14) ;
\draw [shift={(158.24,210.14)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Rectangle [id:dp026479095509071682] 
\draw   (336.61,194.71) -- (397.22,194.71) -- (397.22,219.4) -- (336.61,219.4) -- cycle ;
%Straight Lines [id:da5236391813651351] 
\draw    (123.6,185.46) -- (156.24,185.46) ;
\draw [shift={(158.24,185.46)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da951241427709963] 
\draw    (219.71,183.96) -- (578.79,183.61) ;
\draw [shift={(580.79,183.61)}, rotate = 179.94] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5677734486818795] 
\draw    (218.85,207.67) -- (334.61,208.28) ;
\draw [shift={(336.61,208.29)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da03778045413284792] 
\draw    (397.22,207.61) -- (581.39,207.67) ;
\draw [shift={(583.39,207.67)}, rotate = 180.02] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Rectangle [id:dp9874088035206192] 
\draw   (416.27,219.4) -- (476.88,219.4) -- (476.88,244.08) -- (416.27,244.08) -- cycle ;
%Straight Lines [id:da719219755060643] 
\draw    (476.02,232.97) -- (493.07,233.62) ;
\draw [shift={(495.07,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

% Text Node
\draw (170.55,108.56) node [anchor=north west][inner sep=0.75pt]   [align=left] {3,4};
% Text Node
\draw (264.06,109.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {5,6};
% Text Node
\draw (349.79,107.94) node [anchor=north west][inner sep=0.75pt]   [align=left] {7,9};
% Text Node
\draw (470.74,107.94) node [anchor=north west][inner sep=0.75pt]   [align=left] {12,17};
% Text Node
\draw (174.82,85.72) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
% Text Node
\draw (177.41,60.42) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
% Text Node
\draw (352.32,82.64) node [anchor=north west][inner sep=0.75pt]   [align=left] {7};
% Text Node
\draw (76.23,40.06) node [anchor=north west][inner sep=0.75pt]   [align=left] {head};
% Text Node
\draw (553.41,39.44) node [anchor=north west][inner sep=0.75pt]   [align=left] {tail};
% Text Node
\draw (564.06,59.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (564.06,85.72) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (562.33,106.7) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (45.5,20.51) node [anchor=north west][inner sep=0.75pt]   [align=left] {search path};
% Text Node
\draw (435.12,22.78) node [anchor=north west][inner sep=0.75pt]   [align=left] {update[i] →forward[i] };
% Text Node
\draw (265.32,141.26) node [anchor=north west][inner sep=0.75pt]   [align=left] {original list, 8 to be inserted};
% Text Node
\draw (174.88,224.78) node [anchor=north west][inner sep=0.75pt]   [align=left] {3,4};
% Text Node
\draw (268.39,225.4) node [anchor=north west][inner sep=0.75pt]   [align=left] {5,6};
% Text Node
\draw (354.12,224.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {7,8};
% Text Node
\draw (505.37,224.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {12,17};
% Text Node
\draw (179.15,201.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
% Text Node
\draw (181.74,176.65) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
% Text Node
\draw (356.65,198.86) node [anchor=north west][inner sep=0.75pt]   [align=left] {7};
% Text Node
\draw (80.56,156.28) node [anchor=north west][inner sep=0.75pt]   [align=left] {head};
% Text Node
\draw (595.83,155.67) node [anchor=north west][inner sep=0.75pt]   [align=left] {tail};
% Text Node
\draw (606.49,176.03) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (606.49,201.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (604.76,222.93) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (431.99,223.16) node [anchor=north west][inner sep=0.75pt]   [align=left] {9};
% Text Node
\draw (267.41,246.44) node [anchor=north west][inner sep=0.75pt]   [align=left] {list after insertation};

\end{tikzpicture}
\caption{insert 8 into simple cache-sentive skip list(max array size =2)}
\label{fig:fig2}
\end{figure}

\subsection{Initialization}
The initialization operator is elementary, just create a header with MaxLevel forwards array, and set them to Nil. To simplify the algorithm, we set the header's array with a single value, -inf.

\subsection{Search}
\begin{algorithm}[H]
    \caption{Search Key in simple cache-sentive skip list}
    \KwIn{Key $k$}
    \KwOut{Node containing key or Nil}
    \SetKwFunction{FMain}{search}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FMain{$k$}}{
        $current \gets header$\;

        \For{$i \gets level$ \KwDownTo $0$}{
            \While{$current.forward[i] \neq \text{Nil} \land current.forward[i].Key() \leq k$}{
                $current \gets current.forward[i]$\;
            }
        }

        \KwRet{$current.search\_in\_array(k)$}\;
    }
    \end{algorithm}

As the algorithm shows in Algorithm 1, from line 3 to line 5, it’s very similar to a standard skip list, but in line 4,current.forward[i].Key() returns the least value(at the first position) of the array in the current.forward[i]. Out of the while loop, the current’s forward Key() must be just greater than key, and if the key exists in the data structure, it must be in the current node array, so just search in the array of the current node in line 6.

\subsection{Insertion}
\begin{algorithm}[H]
    \caption{Insert Key into simple cache-sentive skip list}
    \KwIn{Key $k$}
    \KwOut{Nil}
    \SetKwFunction{FMain}{insert}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FMain{$k$}}{
        $update \gets \text{array of size } (max\_level + 1)$\;
        $current \gets header$\;

        \For{$i \gets \texttt{level}$ \KwDownTo $0$}{
            \While{$current.forward[i] \neq \text{Nil} \land current.forward[i].Key() \leq k$}{
                $current \gets current.forward[i]$\;
            }
            $update[i] \gets current$\;
        }

        \If{$current \neq header \land current.is\_full() \land current.array[-1] > k$}{
            $replace \gets current.array.pop()$\;
            $current.insert\_into\_array(k)$\;
            $k \gets replace$\;
        }

        \If{$current \neq header \land \neg current.is\_full()$}{
            $current.insert\_into\_array(k)$\;
        }
        \Else{
            $current \gets current.forward[0]$\;
            \If{$current \neq \text{Nil} \land current \neq header \land \neg current.is\_full()$}{
                $current.insert\_into\_array(k)$\;
                \KwRet{}
            }

            $new\_level \gets random\_level()$\;

            \If{$new\_level > level$}{
                \For{$i \gets level + 1 \KwDownTo new\_level$}{
                    $update[i] \gets header$\;
                }
                $level \gets new\_level$\;
            }

            $new\_node \gets Node([k], new\_level)$\;

            \For{$i \gets 0 $ \KwTo $new\_level$}{
                $new\_node.forward[i] \gets update[i].forward[i]$\;
                $update[i].forward[i] \gets new\_node$\;
            }
        }
    }
    \end{algorithm}
In Algorithm 2, from line 2 to line 7, it’s the same as a standard skip list. However, from line 8 to line 18, It should consider that level 0 nodes have a array. So there are several constraints which cannot be ignored:

\begin{itemize}

\item  If the current node is a header, a new node should be created to insert the key. We don’t want to insert data in the header; otherwise, it will be trouble for the deletion operation. So, in line 8-18, we exclude the header.

There are some cases for insertion:

\item CASE 1: current is not header, but current array size reach the maximum size(current.is\_full() function to check it) and key value is between the least element (first position, Key() return it) and the largest element(last position, current.array[-1]). So in this case, current node’s array is full, we make a small strick to deal with it, we pop the last position element, so the array is not full, and we insert the key in current node array(line 9,10) and it must be full again.then go on the next steps(for example, we replace 9 with 8 , and then insert 9 in another node, see Figure 2).

\item CASE 2: current is not header, current node’s array is not full, just insert the key in the array(line 12, 13). Then the insertion operation is finished.

\item CASE 3: The key is lower than current.forward’s the least value of its array(ines 4-7 has insurance for this), and the key is greater than the largest element of current node’s array, So this key should be inserted into the current’s forward node. We just insert it when the node is not full (from line 15-18), and we do not pop last element like line 9-11, for just to be simple.
\item Other CASES:  we should create a new node and insert the key in its array , and modify the forward pointers(from line 19 to 27)
\end{itemize}

\subsection{Deletion}

\begin{algorithm}[H]
        \caption{Delete key from simple cache-sentive skip list}
        \KwIn{Key $k$}
        \KwOut{True if deleted, False otherwise}
        \SetKwFunction{FMain}{delete}
        \SetKwProg{Fn}{Function}{:}{}
        \Fn{\FMain{$k$}}{
            $update \gets \text{array of size } (max\_level + 1)$\;
            $current \gets header$\;

            \For{$i \gets level$ \KwDownTo $0$}{
                \While{$current.forward[i] \neq \text{Nil} \land current.forward[i].array[-1] < k$}{
                    $current \gets current.forward[i]$\;
                }
                $update[i] \gets current$\;
            }

            $current \gets current.forward[0]$\;
            \If{$current = \text{Nil}$}{
                \KwRet{False}\;
            }
            \Else{
                $res \gets current.delete\_from\_array(k)$\;
                \If{$\neg res$}{
                    \KwRet{False}\;
                }
            }

            \If{$\text{len}(current.array) = 0$}{
                \For{$i \gets$ 0 $\KwTo$ $level$}{
                    \If{$update[i].forward[i] \neq current$}{
                        \textbf{break}; % Use KwBreak instead of Break
                    }
                    $update[i].forward[i] \gets current.forward[i]$\;
                }

                \While{$level > 0 \land header.forward[level] = \text{Nil}$}{
                    $level \gets level - 1$\;
                }
                \KwRet{True}\;
            }
        }
        \end{algorithm}

The deletion algorithm is shown in Algorithm 3, which should be noted that in line 5,  the condition checks whether the current forward array's largest element is less than k, so out of the while loop,  current.forward[0] is the first node whose largest element is equal to or greater than k, which means that if the key exists, it must be in the current node’s forward[0] array. Line 8 to 14, delete the key in the selected array, and Line 15 to 21 checks whether the array is empty, if it is empty, we should delete the node from the data structure.

\section{Evaluation}
\subsection{Experimental Environment}

Here are the overall environments:

\textbf{Hardware}: We chose a MacBook whose CPU is Apple M2, and 16 GB of memory. and another server computer with Intel(R) Core(TM) i7-6700 CPU @ 3.40GHz , 24G ddr4 2133 memory. We use this server computer not only to test the performance, but also to test the CPU cache miss.

\textbf{Compiler}: We complete the algorithm in cpp codes, The test program is compiled by g++ with O3 optimization option.

\textbf{Benchmark}:  Because insert data in skip list, will more possibily cause CPU cache missing. so we test insertion with random data. and also give search test. The scale of data elements is from 100 to 300000. We do not present the search performance because the performance gap is negligible.

\subsection{Performace}
\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=10pt,
    width=14cm,
    height=9cm,
    enlarge x limits=0.1,
    xlabel={Size},
    ylabel={Time (µs)},
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    legend style={at={(0.5,-0.15)},anchor=north,legend columns=2},
    nodes near coords,
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west},
    ymin=0,
    ymajorgrids=true,
    grid style=dashed
]
\addplot+[style={blue,fill=blue!30}] coordinates {
    (100,19) (1000,222) (5000,1383) (10000,2654)  (20000,4474) (50000,11040) (200000,51209) (250000,66618) (300000,81313)
};
\addplot+[style={red,fill=red!30}] coordinates {
    (100,14) (1000,174) (5000,994) (10000,2070)  (20000,2936) (50000,6986) (200000,30934) (250000,41203) (300000,51843)
};

\legend{SkipList, SCSL}
\end{axis}
\end{tikzpicture}
\caption{Insertion Time Comparison Between SkipList and SCSL at Different Scales(smaller is better) in Macos}
\end{figure}

\begin{figure}[htbp]
\begin{tikzpicture}
\begin{axis}[
    width=14cm,
    height=8cm,
    ybar,
    bar width=12pt,
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    xlabel={Data Size},
    ylabel={Time (µs)},
    legend style={at={(0.5,-0.2)},anchor=north,legend columns=-1},
    enlarge x limits=0.08,
    ymin=0,
    grid=major,
    nodes near coords,
    nodes near coords style={font=\small, anchor=west, rotate=90, xshift=4pt},
]

\addplot coordinates {(100,62) (1000,719) (5000,2561) (10000,4532) (20000,8075) (50000,30651) (200000,150126) (250000,206036) (300000,249135)};
\addplot coordinates {(100,40) (1000,294) (5000,1760) (10000,2531) (20000,4238) (50000,10462) (200000,54598) (250000,73624) (300000,92321)};

\legend{SkipList, SCSL}
\end{axis}
\end{tikzpicture}
\caption{Insertion Time Comparison Between SkipList and SCSL at Different Scales(smaller is better) in Server}
\end{figure}

We evaluated the standard skip list and SCSL with a maximum level of 16. Figure 3 presents the insertion performance comparison between the standard skip list and simple cache skip list in a Macbook. It shows that under small scale of data (< 1000) simple cache skip list can speed up to 1.28~1.39 times, and under medium scale (over 20000) , it can speed up to 1.55~1.65 times, as the scale increasing, the more benefit for performance. Figure 4 also shows that, in server computer, the simple cache skip list can speed up even 3 times.
\begin{table}
\begin{tabular}{lrrr}
\toprule
Test Case & Cache References & Cache Misses & Cache Miss Rate \\
\midrule
SCSL & 51,567,218 & 459,636 & 0.89\% \\
Standard Skip List & 142,249,678 & 47,251,323 & 33.22\% \\
\bottomrule
\end{tabular}
\caption{Cache Performance Comparison Between SCSL and standard Skip list in server computer}
\end{table}

As shown in the table above(table 1), the standard skip list in the test achieves a 33.22\% cache-miss rate, whereas SCSL has only a 0.89\% cache-miss rate. It also proves that adding arrays to data nodes can work very well.

\section{Conclusions}
We present a new method to implement a cache-sensitive skip list, SCSL, which only changes a single element in the data-level nodes to an array. SCSL effectively leverages CPU caches by using data stored in continuous memory, and the algorithm is simple. Additionally, the performance results are also significant.
\begin{thebibliography}{9} 
\bibitem{ref1}
      Skip Lists: A Probabilistic Alternative to Balanced Trees
\bibitem{ref2}
      Google. LevelDB. Available online: https://github.com/google/leveldb (accessed on 20 July 2023).
\bibitem{ref3}
      Facebook. RocksDB. Available online: http://rocksdb.org/ (accessed on 20 July 2023).
\bibitem{ref4}
      Apache. Welcome to Apache HBase™. Available online: https://hbase.apache.org/ (accessed on 20 July 2023).
\bibitem{ref5}
      Cache-Sensitive Skip List: Efficient Range Queries on modern CPUs - informatik.hu-berlin.de.
\bibitem{ref6}
      ESL: A High-Performance Skiplist with Express Lane  https://www.mdpi.com/2076-3417/13/17/9925
\bibitem{ref7}
	Redis, Accessed: 2024-01-09.
\end{thebibliography}
\end{document}

### 2025-04-27 skiplist.py

@@ -1,0 +1,151 @@
+import random
+
+class Node:
+    def __init__(self, key, value, level):
+        # 每个节点包含一个键值对和指向不同层的下一个节点的指针数组
+        self.key = key
+        self.value = value
+        # forward数组存储该节点在每一层的下一个节点
+        self.forward = [None] * (level + 1)
+
+class SkipList:
+    def __init__(self, max_level=16, p=0.5):
+        # 最大层数
+        self.max_level = max_level
+        # 用于随机层数的概率因子
+        self.p = p
+        # 当前跳表的最大层数
+        self.level = 0
+        # 头节点，不存储实际数据
+        self.header = Node(None, None, max_level)
+    
+    # 随机生成层数
+    def random_level(self):
+        level = 0
+        while random.random() < self.p and level < self.max_level:
+            level += 1
+        return level
+    
+    # 插入键值对
+    def insert(self, key, value):
+        # 用于记录每一层需要更新的节点
+        update = [None] * (self.max_level + 1)
+        current = self.header
+        
+        # 从最高层开始搜索
+        for i in range(self.level, -1, -1):
+            while current.forward[i] and current.forward[i].key < key:
+                current = current.forward[i]
+            update[i] = current
+        
+        # 到达第0层，并且向前移动
+        current = current.forward[0]
+        
+        # 如果键已存在，则更新值
+        if current and current.key == key:
+            current.value = value
+        else:
+            # 生成一个随机层数
+            new_level = self.random_level()
+            
+            # 如果新层数大于当前最大层数，需要更新头节点
+            if new_level > self.level:
+                for i in range(self.level + 1, new_level + 1):
+                    update[i] = self.header
+                self.level = new_level
+            
+            # 创建新节点
+            new_node = Node(key, value, new_level)
+            
+            # 更新每一层的指针
+            for i in range(new_level + 1):
+                new_node.forward[i] = update[i].forward[i]
+                update[i].forward[i] = new_node
+    
+    # 查找键对应的值
+    def search(self, key):
+        current = self.header
+        
+        # 从最高层开始搜索
+        for i in range(self.level, -1, -1):
+            while current.forward[i] and current.forward[i].key < key:
+                current = current.forward[i]
+        
+        # 到达第0层，并且向前移动
+        current = current.forward[0]
+        
+        # 如果找到键，则返回对应的值
[…]

### 2025-04-27 skiplistarr.cpp

@@ -1,0 +1,269 @@
+#include <iostream>
+#include <vector>
+#include <algorithm>
+#include <random>
+#include <climits>
+
+class Node {
+private:
+    std::vector<int> array;
+    int max_array_size;
+
+public:
+    std::vector<Node*> forward;
+
+    Node(const std::vector<int>& arr, int level, int max_array_size = 2) 
+        : array(arr), max_array_size(max_array_size) {
+        forward.resize(level + 1, nullptr);
+    }
+
+    int First() const {
+        return array[0];
+    }
+
+    int Last() const {
+        return array.back();
+    }
+    void Pop() {
+        array.pop_back();
+    }
+    bool insert_into_array(int key) {
+        // Find position to insert while maintaining sorted order
+        auto pos = std::lower_bound(array.begin(), array.end(), key);
+        array.insert(pos, key);
+        return true;
+    }
+
+    int search_in_array(int key) const {
+        auto pos = std::lower_bound(array.begin(), array.end(), key);
+        if (pos != array.end() && *pos == key) {
+            return key;
+        }
+        return -1; // Not found, using -1 as "null" equivalent
+    }
+
+    bool delete_from_array(int key) {
+        auto pos = std::lower_bound(array.begin(), array.end(), key);
+        if (pos != array.end() && *pos == key) {
+            array.erase(pos);
+            return true;
+        }
+        return false;
+    }
+
+    bool is_full() const {
+        return array.size() >= max_array_size;
+    }
+    bool is_empty() const {
+        return array.empty();
+    }
+    friend std::ostream& operator<<(std::ostream& os, const Node& node) {
+        os << "(";
+        for (size_t i = 0; i < node.array.size(); ++i) {
+            os << node.array[i];
+            if (i < node.array.size() - 1) {
+                os << ", ";
+            }
+        }
+        os << ")";
+        return os;
+    }
+};
+
+class SkipListArr {
+private:
+    int max_level;
+    double p;
+    int level;
+    Node* header;
+    std::mt19937 gen;
+    std::uniform_real_distribution<> dis;
+
+public:
+    SkipListArr(int max_level = 16, double p = 0.5) 
+        : max_level(max_level), p(p), level(0), gen(std::random_device()()), dis(0.0, 1.0) {
+        std::vector<int> headerKey = {INT_MIN}; // Using INT_MIN as negative infinity
+        header = new Node(headerKey, max_level);
+    }
+
+    ~SkipListArr() {
[…]

### 2025-04-27 skiplistarr.py

@@ -1,0 +1,197 @@
+import random, bisect
+
+class Node:
+    def __init__(self, arr, level,max_array_size=2):
+        # 每个节点包含一个键值对和指向不同层的下一个节点的指针数组
+        self.array = arr
+        self.max_array_size = max_array_size
+        # forward数组存储该节点在每一层的下一个节点
+        self.forward = [None] * (level + 1)
+    def __str__(self) -> str:
+        return str(self.array)
+    def Key(self):
+        return self.array[0]
+    def insert_into_array(self, key):
+        # 使用bisect模块保持数组有序
+        index = bisect.bisect_left(self.array, key)
+        self.array.insert(index, key)
+        return True
+    def search_in_array(self, key):
+        # 在数组中查找键
+        index = bisect.bisect_left(self.array, key)
+        if index < len(self.array) and self.array[index] == key:
+            return key
+        return None
+    def delete_from_array(self, key):
+        # 从数组中删除键
+        index = bisect.bisect_left(self.array, key)
+        if index < len(self.array) and self.array[index] == key:
+            self.array.pop(index)
+            return True
+        return False
+    def is_full(self):
+        return len(self.array) >= self.max_array_size
+    
+            
+class SkipList:
+    def __init__(self, max_level=16, p=0.5):
+        # 最大层数
+        self.max_level = max_level
+        # 用于随机层数的概率因子
+        self.p = p
+        # 当前跳表的最大层数
+        self.level = 0
+        # 头节点，不存储实际数据
+        self.header = Node([float('-inf')], max_level)
+    
+    # 随机生成层数
+    def random_level(self):
+        level = 0
+        while random.random() < self.p and level < self.max_level:
+            level += 1
+        return level
+    
+    # 插入键值对
+    def insert(self, key):
+        # 用于记录每一层需要更新的节点
+        update = [None] * (self.max_level + 1)
+        current = self.header
+        
+        # 从最高层开始搜索
+        for i in range(self.level, -1, -1):
+            while current.forward[i] and current.forward[i].Key() <= key:
+                current = current.forward[i]
+            update[i] = current
+        
+        # 到达第0层, 恰好array[0] < key, 而forward > key 或者为None
+        # 恰好满, 而且还在范围内
+        if current and current != self.header and current.is_full() and current.array[-1] > key:
+            replace = current.array.pop()
+            current.insert_into_array(key)
+            key = replace
[…]

### 2025-04-27 test.cpp

@@ -1,0 +1,479 @@
+#include <iostream>
+#include <vector>
+#include <random>
+#include <chrono>
+#include <algorithm>
+#include <limits>
+// 常量定义
+const float P = 0.5f;     // 升级概率
+const int MAX_LEVEL = 16; // SkipList 最大层数
+const int MAX_LEN = 128 ;
+// SkipList 节点定义
+class SkipListNode {
+public:
+    int value;
+    // forward[i] 表示当前节点在 i 层的下一个节点
+    std::vector<SkipListNode*> forward;
+
+    SkipListNode(int val, int level) : value(val), forward(level + 1, nullptr) {}
+};
+
+// SkipList 实现
+class SkipList {
+private:
+    int level;                // 当前最高层数
+    SkipListNode* header;     // 哨兵节点
+    std::mt19937 rng;         // 随机数生成器
+    std::uniform_real_distribution<float> dist; // [0, 1) 均匀分布
+
+public:
+    SkipList() : level(0), header(new SkipListNode(-1, MAX_LEVEL)), 
+                 rng(std::random_device{}()), dist(0.0f, 1.0f) {}
+
+    ~SkipList() {
+        // 释放所有节点
+        SkipListNode* node = header;
+        while (node) {
+            SkipListNode* next = node->forward[0];
+            delete node;
+            node = next;
+        }
+    }
+
+    // 随机生成层数
+    int randomLevel() {
+        int lvl = 0;
+        while (dist(rng) < P && lvl < MAX_LEVEL)
+            ++lvl;
+        return lvl;
+    }
+
+    // 插入操作
+    void insert(int value) {
+        std::vector<SkipListNode*> update(MAX_LEVEL + 1, nullptr);
+        SkipListNode* x = header;
+
+        // 从最高层开始查找插入位置
+        for (int i = level; i >= 0; --i) {
+            while (x->forward[i] != nullptr && x->forward[i]->value < value) {
+                x = x->forward[i];
+            }
+            update[i] = x;
+        }
+        x = x->forward[0];
+
+        // 随机生成新节点层数
+        int lvl = randomLevel();
+        if (lvl > level) {
+            // 对于新增加的层，初始化 update 为 header
+            for (int i = level + 1; i <= lvl; ++i)
+                update[i] = header;
+            level = lvl;
+        }
+        // 创建新节点，并将各层指针接入链表
+        SkipListNode* newNode = new SkipListNode(value, lvl);
[…]

### 2025-04-27 test1.cpp

@@ -1,0 +1,463 @@
+#include <iostream>
+#include <vector>
+#include <random>
+#include <chrono>
+#include <algorithm>
+#include <limits>
+// 常量定义
+const float P = 0.5f;     // 升级概率
+const int MAX_LEVEL = 16; // SkipList 最大层数
+const int MAX_LEN = 128 ;
+// SkipList 节点定义
+class SkipListNode {
+public:
+    int value;
+    // forward[i] 表示当前节点在 i 层的下一个节点
+    std::vector<SkipListNode*> forward;
+
+    SkipListNode(int val, int level) : value(val), forward(level + 1, nullptr) {}
+};
+
+// SkipList 实现
+class SkipList {
+private:
+    int level;                // 当前最高层数
+    SkipListNode* header;     // 哨兵节点
+    std::mt19937 rng;         // 随机数生成器
+    std::uniform_real_distribution<float> dist; // [0, 1) 均匀分布
+
+public:
+    SkipList() : level(0), header(new SkipListNode(-1, MAX_LEVEL)), 
+                 rng(std::random_device{}()), dist(0.0f, 1.0f) {}
+
+    ~SkipList() {
+        // 释放所有节点
+        SkipListNode* node = header;
+        while (node) {
+            SkipListNode* next = node->forward[0];
+            delete node;
+            node = next;
+        }
+    }
+
+    // 随机生成层数
+    int randomLevel() {
+        int lvl = 0;
+        while (dist(rng) < P && lvl < MAX_LEVEL)
+            ++lvl;
+        return lvl;
+    }
+
+    // 插入操作
+    void insert(int value) {
+        std::vector<SkipListNode*> update(MAX_LEVEL + 1, nullptr);
+        SkipListNode* x = header;
+
+        // 从最高层开始查找插入位置
+        for (int i = level; i >= 0; --i) {
+            while (x->forward[i] != nullptr && x->forward[i]->value < value) {
+                x = x->forward[i];
+            }
+            update[i] = x;
+        }
+        x = x->forward[0];
+
+        // 随机生成新节点层数
+        int lvl = randomLevel();
+        if (lvl > level) {
+            // 对于新增加的层，初始化 update 为 header
+            for (int i = level + 1; i <= lvl; ++i)
+                update[i] = header;
+            level = lvl;
+        }
+        // 创建新节点，并将各层指针接入链表
+        SkipListNode* newNode = new SkipListNode(value, lvl);
[…]

### 2025-04-27 test2.cpp

@@ -1,0 +1,464 @@
+#include <iostream>
+#include <vector>
+#include <random>
+#include <chrono>
+#include <algorithm>
+#include <limits>
+// 常量定义
+const float P = 0.5f;     // 升级概率
+const int MAX_LEVEL = 16; // SkipList 最大层数
+const int MAX_LEN = 128 ;
+// SkipList 节点定义
+class SkipListNode {
+public:
+    int value;
+    // forward[i] 表示当前节点在 i 层的下一个节点
+    std::vector<SkipListNode*> forward;
+
+    SkipListNode(int val, int level) : value(val), forward(level + 1, nullptr) {}
+};
+
+// SkipList 实现
+class SkipList {
+private:
+    int level;                // 当前最高层数
+    SkipListNode* header;     // 哨兵节点
+    std::mt19937 rng;         // 随机数生成器
+    std::uniform_real_distribution<float> dist; // [0, 1) 均匀分布
+
+public:
+    SkipList() : level(0), header(new SkipListNode(-1, MAX_LEVEL)), 
+                 rng(std::random_device{}()), dist(0.0f, 1.0f) {}
+
+    ~SkipList() {
+        // 释放所有节点
+        SkipListNode* node = header;
+        while (node) {
+            SkipListNode* next = node->forward[0];
+            delete node;
+            node = next;
+        }
+    }
+
+    // 随机生成层数
+    int randomLevel() {
+        int lvl = 0;
+        while (dist(rng) < P && lvl < MAX_LEVEL)
+            ++lvl;
+        return lvl;
+    }
+
+    // 插入操作
+    void insert(int value) {
+        std::vector<SkipListNode*> update(MAX_LEVEL + 1, nullptr);
+        SkipListNode* x = header;
+
+        // 从最高层开始查找插入位置
+        for (int i = level; i >= 0; --i) {
+            while (x->forward[i] != nullptr && x->forward[i]->value < value) {
+                x = x->forward[i];
+            }
+            update[i] = x;
+        }
+        x = x->forward[0];
+
+        // 随机生成新节点层数
+        int lvl = randomLevel();
+        if (lvl > level) {
+            // 对于新增加的层，初始化 update 为 header
+            for (int i = level + 1; i <= lvl; ++i)
+                update[i] = header;
+            level = lvl;
+        }
+        // 创建新节点，并将各层指针接入链表
+        SkipListNode* newNode = new SkipListNode(value, lvl);
[…]

### 2025-05-07 simple cache-sentive skip list/main.tex
add paper

--- 2025-04-27 paper.tex
@@
-\documentclass{article}
+% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
+% https://www.acm.org/publications/proceedings-template
+% The ACM Latex guide provides further information about the ACM template
 
-\newcommand{\keywords}[1]{\par\noindent\textbf{Keywords:} #1}
-% Language setting
-% Replace `english' with e.g. `spanish' to change the document language
-\usepackage[english]{babel}
+\documentclass[sigconf, nonacm, letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{acmart}
 
-% Set page size and margins
-% Replace `letterpaper' with `a4paper' for UK/EU standard size
-\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-\usepackage{tikz}
+%% The following content must be adapted for the final version
+% paper-specific
+\newcommand\vldbdoi{XX.XX/XXX.XX}
+\newcommand\vldbpages{XXX-XXX}
+% issue-specific
+\newcommand\vldbvolume{19}
+\newcommand\vldbissue{1}
+\newcommand\vldbyear{2025}
+% should be fine as it is
+\newcommand\vldbauthors{\authors}
+\newcommand\vldbtitle{\shorttitle} 
+% leave empty if no availability url should be set
+\newcommand\vldbavailabilityurl{}
+% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
+\newcommand\vldbpagestyle{plain}
+
+\usepackage{adjustbox}
 \usepackage{pgfplots}
@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
 \SetKw{KwDownTo}{down to}
+\begin{document}
+\title{Simple Cache-sensitive Skip list}
 
-\title{simple cache-sentive skip list}
-\author{Yuchang Ke \\
- \texttt{aceking.ke@gmail.com}
-\and Bill Lv \\
-\texttt{ideaalloc@gmail.com}
-\and Weijie Zhang\\
-\texttt{zhangweijie@gmail.com}}
+%%
+%% The "author" command and its associated commands are used to define the authors and their affiliations.
+\author{Yuchang Ke}
+\affiliation{%
+  \institution{independent researcher}
+  \streetaddress{No. 12, Guandong Street, Hongshan District, Wuhan, Hubei Province.}
+  \city{Wuhan}
+  \state{China}
+  \postcode{430073}
+}
+\email{aceking.ke@gmail.com}
 
-\begin{document}
-\maketitle
+\author{Bill Lv}
+\email{ideaalloc@gmail.com}
 
+\author{Weijie Zhang}
+\email{zhangweijie@gmail.com}
+
+%%
+%% The abstract is a short summary of the work to be presented in the
+%% article.
 \begin{abstract}
@@
 This design can be used not only in in-memory databases or key-value stores, but also in embedded systems.
+here is \href{https://github.com/acekingke/simpleCacheSentiveSkiplist}{github link}
+\keywords{skiplist; cache-sensitive; index structure}
 
-\keywords{skiplist; cache-sensitive; index structure}
 \end{abstract}
+
+\maketitle
+
+%%% do not modify the following VLDB block %%
+%%% VLDB block start %%%
+\pagestyle{\vldbpagestyle}
+\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
+\vldbauthors. \vldbtitle. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
+\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
+\endgroup
+\begingroup
+\renewcommand\thefootnote{}\footnote{\noindent
+This work is licensed under the Creative Commons BY-NC-ND 4.0 International License.
+Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license.
+For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}.
+Copyright is held by the owner/author(s).
+Publication rights licensed to the VLDB Endowment.
+\\
+\raggedright Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
+ISSN 2150-8097. \\
+\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
+}\addtocounter{footnote}{-1}\endgroup
+%%% VLDB block end %%%
+
+%%% do not modify the following VLDB block %%
+%%% VLDB block start %%%
+\ifdefempty{\vldbavailabilityurl}{}{
+\vspace{.3cm}
+\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
+The source code, data, and/or other artifacts have been made available at \url{\vldbavailabilityurl}.
+\endgroup
+}
+%%% VLDB block end %%%
 
@@
 
-\begin{figure}[h]
+\begin{figure}
   \centering
-\includegraphics[width=0.5\linewidth]{skiplist.png}
+  \includegraphics[width=\linewidth]{figures/skiplist.png}
 \caption{A simple cache-sensitive skip list}
-\label{fig:fig1}
+  \label{fig:skiplist}
 \end{figure}
+
 Our key contributions include: 1.
@@
 
-\begin{figure}[ht]
+\begin{figure}
       \centering
-\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,302); %set diagram left start at 0, and has height of 302
-
-%Shape: Rectangle [id:dp802121456728152] 
-\draw   (57.79,105.64) -- (118.41,105.64) -- (118.41,130.32) -- (57.79,130.32) -- cycle ;
-%Shape: Rectangle [id:dp9825705095547612] 
-\draw   (332.28,103.17) -- (392.89,103.17) -- (392.89,127.86) -- (332.28,127.86) -- cycle ;
-%Shape: Rectangle [id:dp248949237262718] 
-\draw   (246.56,103.79) -- (307.17,103.79) -- (307.17,128.47) -- (246.56,128.47) -- cycle ;
-%Shape: Rectangle [id:dp1628354408576529] 
-\draw   (153.04,104.41) -- (213.65,104.41) -- (213.65,129.09) -- (153.04,129.09) -- cycle ;
-%Shape: Rectangle [id:dp000018829587681290505] 
-\draw   (57.79,56.27) -- (118.41,56.27) -- (118.41,80.96) -- (57.79,80.96) -- cycle ;
-%Shape: Rectangle [id:dp247562625981687] 
-\draw   (57.79,80.96) -- (118.41,80.96) -- (118.41,105.64) -- (57.79,105.64) -- cycle ;
-%Shape: Rectangle [id:dp2644216550992282] 
-\draw   (540.96,104.41) -- (601.57,104.41) -- (601.57,129.09) -- (540.96,129.09) -- cycle ;
-%Shape: Rectangle [id:dp8347359895416517] 
-\draw   (540.96,55.04) -- (601.57,55.04) -- (601.57,79.72) -- (540.96,79.72) -- cycle ;
-%Shape: Rectangle [id:dp6823901202027933] 
-\draw   (540.96,79.72) -- (601.57,79.72) -- (601.57,104.41) -- (540.96,104.41) -- cycle ;
-%Shape: Rectangle [id:dp379773497534003] 
-\draw   (153.04,79.72) -- (213.65,79.72) -- (213.65,104.41) -- (153.04,104.41) -- cycle ;
-%Shape: Rectangle [id:dp8262463980956687] 
-\draw   (153.04,55.04) -- (213.65,55.04) -- (213.65,79.72) -- (153.04,79.72) -- cycle ;
-%Shape: Rectangle [id:dp618442800182132] 
-\draw   (454.37,103.17) -- (514.98,103.17) -- (514.98,127.86) -- (454.37,127.86) -- cycle ;
-%Straight Lines [id:da18234761053431092] 
-\draw    (118.41,119.22) -- (151.04,119.22) ;
-\draw [shift={(153.04,119.22)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da17691354593928432] 
-\draw    (213.65,117.98) -- (246.29,117.98) ;
-\draw [shift={(248.29,117.98)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da06545360607750506] 
-\draw    (306.3,116.13) -- (332.01,116.13) ;
-\draw [shift={(334.01,116.13)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da8917793267177494] 
-\draw    (392.89,116.75) -- (452.37,117.34) ;
-\draw [shift={(454.37,117.36)}, rotate = 180.58] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da6270688079351094] 
-\draw    (514.98,116.13) -- (538.96,116.7) ;
-\draw [shift={(540.96,116.75)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da16483082426708995] 
-\draw    (119.27,93.91) -- (151.91,93.91) ;
-\draw [shift={(153.91,93.91)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Shape: Rectangle [id:dp8280971824764716] 
-\draw   (332.28,78.49) -- (392.89,78.49) -- (392.89,103.17) -- (332.28,103.17) -- cycle ;
-%Straight Lines [id:da6251582090553987] 
-\draw    (119.27,69.23) -- (151.91,69.23) ;
-\draw [shift={(153.91,69.23)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da906622887317923] 
-\draw    (214.52,67.38) -- (536.36,67.38) ;
-\draw [shift={(538.36,67.38)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da1247883464855224] 
-\draw    (214.52,91.45) -- (330.28,92.05) ;
-\draw [shift={(332.28,92.06)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da5312111106538793] 
-\draw    (392.03,91.45) -- (538.96,91.45) ;
-\draw [shift={(540.96,91.45)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Curve Lines [id:da7690346774156931] 
-\draw    (107.15,66.76) .. controls (141.78,48.25) and (163.43,87.74) .. (198.07,69.23) ;
-%Curve Lines [id:da09969258339888487] 
-\draw    (198.07,69.23) .. controls (232.7,50.72) and (171.22,109.34) .. (205.86,90.83) ;
-%Curve Lines [id:da17301735066569246] 
-\draw    (205.86,90.83) .. controls (240.5,72.32) and (331.41,113.66) .. (366.05,95.15) ;
-%Curve Lines [id:da04935924618461396] 
-\draw    (361.72,97) .. controls (396.36,78.49) and (358.26,135.26) .. (392.89,116.75) ;
-%Curve Lines [id:da43861108104506963] 
-\draw    (52.6,38.99) .. controls (87.23,20.48) and (72.51,85.27) .. (107.15,66.76) ;
-%Shape: Ellipse [id:dp551323556779669] 
-\draw   (410.21,92.06) ..
-controls (410.21,69.57) and (417.19,51.33) ..
-(425.8,51.33) ..
-controls (434.4,51.33) and (441.38,69.57) ..
-(441.38,92.06) ..
-controls (441.38,114.56) and (434.4,132.79) ..
-(425.8,132.79) ..
-controls (417.19,132.79) and (410.21,114.56) ..
-(410.21,92.06) -- cycle ;
-%Straight Lines [id:da9115207752269137] 
-\draw    (445.71,32.82) -- (427.26,49.97) ;
-\draw [shift={(425.8,51.33)}, rotate = 317.09] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Shape: Rectangle [id:dp44944938443713855] 
-\draw   (62.12,221.87) -- (122.73,221.87) -- (122.73,246.55) -- (62.12,246.55) -- cycle ;
-%Shape: Rectangle [id:dp8751335667917544] 
-\draw   (336.61,219.4) -- (397.22,219.4) -- (397.22,244.08) -- (336.61,244.08) -- cycle ;
-%Shape: Rectangle [id:dp2257346710215089] 
-\draw   (250.89,220.01) -- (311.5,220.01) -- (311.5,244.7) -- (250.89,244.7) -- cycle ;
-%Shape: Rectangle [id:dp8771184949651254] 
-\draw   (157.37,220.63) -- (217.98,220.63) -- (217.98,245.32) -- (157.37,245.32) -- cycle ;
-%Shape: Rectangle [id:dp5789469841235695] 
-\draw   (62.12,172.5) -- (122.73,172.5) -- (122.73,197.18) -- (62.12,197.18) -- cycle ;
-%Shape: Rectangle [id:dp5624687649592586] 
-\draw   (62.12,197.18) -- (122.73,197.18) -- (122.73,221.87) -- (62.12,221.87) -- cycle ;
-%Shape: Rectangle [id:dp13120546674792055] 
-\draw   (583.39,220.63) -- (644,220.63) -- (644,245.32) -- (583.39,245.32) -- cycle ;
-%Shape: Rectangle [id:dp18910975661576046] 
-\draw   (583.39,171.26) -- (644,171.26) -- (644,195.95) -- (583.39,195.95) -- cycle ;
-%Shape: Rectangle [id:dp968839873549274] 
-\draw   (583.39,195.95) -- (644,195.95) -- (644,220.63) -- (583.39,220.63) -- cycle ;
-%Shape: Rectangle [id:dp5100738159249718] 
-\draw   (157.37,195.95) -- (217.98,195.95) -- (217.98,220.63) -- (157.37,220.63) -- cycle ;
-%Shape: Rectangle [id:dp5130816669129519] 
-\draw   (157.37,171.26) -- (217.98,171.26) -- (217.98,195.95) -- (157.37,195.95) -- cycle ;
-%Shape: Rectangle [id:dp10069788621732956] 
-\draw   (495.07,219.4) -- (555.68,219.4) -- (555.68,244.08) -- (495.07,244.08) -- cycle ;
-%Straight Lines [id:da7506949131852723] 
-\draw    (122.73,235.44) -- (155.37,235.44) ;
-\draw [shift={(157.37,235.44)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da5055411274108006] 
-\draw    (217.98,234.21) -- (250.62,234.21) ;
-\draw [shift={(252.62,234.21)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da7559298876477776] 
-\draw    (310.63,232.36) -- (336.34,232.36) ;
-\draw [shift={(338.34,232.36)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da08581070094109111] 
-\draw    (397.22,232.97) -- (414.27,233.62) ;
-\draw [shift={(416.27,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da5858905620692174] 
-\draw    (557.41,232.36) -- (581.39,232.93) ;
-\draw [shift={(583.39,232.97)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da32674036346427937] 
-\draw    (123.6,210.14) -- (156.24,210.14) ;
-\draw [shift={(158.24,210.14)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Shape: Rectangle [id:dp026479095509071682] 
-\draw   (336.61,194.71) -- (397.22,194.71) -- (397.22,219.4) -- (336.61,219.4) -- cycle ;
-%Straight Lines [id:da5236391813651351] 
-\draw    (123.6,185.46) -- (156.24,185.46) ;
-\draw [shift={(158.24,185.46)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da951241427709963] 
-\draw    (219.71,183.96) -- (578.79,183.61) ;
-\draw [shift={(580.79,183.61)}, rotate = 179.94] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da5677734486818795] 
-\draw    (218.85,207.67) -- (334.61,208.28) ;
-\draw [shift={(336.61,208.29)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Straight Lines [id:da03778045413284792] 
-\draw    (397.22,207.61) -- (581.39,207.67) ;
-\draw [shift={(583.39,207.67)}, rotate = 180.02] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-%Shape: Rectangle [id:dp9874088035206192] 
-\draw   (416.27,219.4) -- (476.88,219.4) -- (476.88,244.08) -- (416.27,244.08) -- cycle ;
-%Straight Lines [id:da719219755060643] 
-\draw    (476.02,232.97) -- (493.07,233.62) ;
-\draw [shift={(495.07,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
-controls (6.95,-1.4) and (3.31,-0.3) ..
-(0,0) ..
-controls (3.31,0.3) and (6.95,1.4) ..
-(10.93,3.29)   ;
-
-% Text Node
-\draw (170.55,108.56) node [anchor=north west][inner sep=0.75pt]   [align=left] {3,4};
-% Text Node
-\draw (264.06,109.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {5,6};
-% Text Node
-\draw (349.79,107.94) node [anchor=north west][inner sep=0.75pt]   [align=left] {7,9};
-% Text Node
-\draw (470.74,107.94) node [anchor=north west][inner sep=0.75pt]   [align=left] {12,17};
-% Text Node
-\draw (174.82,85.72) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
-% Text Node
-\draw (177.41,60.42) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
-% Text Node
-\draw (352.32,82.64) node [anchor=north west][inner sep=0.75pt]   [align=left] {7};
-% Text Node
-\draw (76.23,40.06) node [anchor=north west][inner sep=0.75pt]   [align=left] {head};
-% Text Node
-\draw (553.41,39.44) node [anchor=north west][inner sep=0.75pt]   [align=left] {tail};
-% Text Node
-\draw (564.06,59.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (564.06,85.72) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (562.33,106.7) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (45.5,20.51) node [anchor=north west][inner sep=0.75pt]   [align=left] {search path};
-% Text Node
-\draw (435.12,22.78) node [anchor=north west][inner sep=0.75pt]   [align=left] {update[i] →forward[i] };
-% Text Node
-\draw (265.32,141.26) node [anchor=north west][inner sep=0.75pt]   [align=left] {original list, 8 to be inserted};
-% Text Node
-\draw (174.88,224.78) node [anchor=north west][inner sep=0.75pt]   [align=left] {3,4};
-% Text Node
-\draw (268.39,225.4) node [anchor=north west][inner sep=0.75pt]   [align=left] {5,6};
-% Text Node
-\draw (354.12,224.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {7,8};
-% Text Node
-\draw (505.37,224.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {12,17};
-% Text Node
-\draw (179.15,201.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
-% Text Node
-\draw (181.74,176.65) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
-% Text Node
-\draw (356.65,198.86) node [anchor=north west][inner sep=0.75pt]   [align=left] {7};
-% Text Node
-\draw (80.56,156.28) node [anchor=north west][inner sep=0.75pt]   [align=left] {head};
-% Text Node
-\draw (595.83,155.67) node [anchor=north west][inner sep=0.75pt]   [align=left] {tail};
-% Text Node
-\draw (606.49,176.03) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (606.49,201.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (604.76,222.93) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (431.99,223.16) node [anchor=north west][inner sep=0.75pt]   [align=left] {9};
-% Text Node
-\draw (267.41,246.44) node [anchor=north west][inner sep=0.75pt]   [align=left] {list after insertation};
-
-\end{tikzpicture}
+  \includegraphics[width=\linewidth]{figures/skipinsert.jpg}
 \caption{insert 8 into simple cache-sentive skip list(max array size =2)}
@@
 \subsection{Search}
-\begin{algorithm}[H]
+\begin{algorithm}
     \caption{Search Key in simple cache-sentive skip list}
@@
 \subsection{Insertion}
-\begin{algorithm}[H]
+\begin{algorithm}
     \caption{Insert Key into simple cache-sentive skip list}
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}
         \caption{Delete key from simple cache-sentive skip list}
@@
 \subsection{Performace}
-\begin{figure}[htbp]
+\begin{figure}
 \centering
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.6]
 \begin{axis}[
@@
 
-\begin{figure}[htbp]
-\begin{tikzpicture}
+\begin{figure}
+\begin{tikzpicture}[scale=0.6]
 \begin{axis}[
@@
 Figure 4 also shows that, in server computer, the simple cache skip list can speed up even 3 times.
-\begin{table}
+\begin{table*}[t]
 \begin{tabular}{lrrr}
 \toprule
-Test Case & Cache References & Cache Misses & Cache Miss Rate \\
+Test Case & Cache References & Cache Misses & Cache Misses Rate \\
 \midrule
-SCSL & 51,567,218 & 459,636 & 0.89\% \\
-Standard Skip List & 142,249,678 & 47,251,323 & 33.22\% \\
+\verb|SCSL| & 51,567,218 & 459,636 & 0.89\% \\
+\verb|Standard Skip List| & 142,249,678 & 47,251,323 & 33.22\% \\
 \bottomrule
@@
 \caption{Cache Performance Comparison Between SCSL and standard Skip list in server computer}
-\end{table}
-
+\end{table*}
 As shown in the table above(table 1), the standard skip list in the test achieves a 33.22\% cache-miss rate, whereas SCSL has only a 0.89\% cache-miss rate.

### 2025-05-27 paper.tex
affiliation info
test
add affiliation
state should be country
suggestions to paper \[not complete\]

@@
 
-\newcommand{\keywords}[1]{\par\noindent\textbf{Keywords:} #1}
 % Language setting
-% Replace `english' with e.g. `spanish' to change the document language
 \usepackage[english]{babel}
@@
 % Set page size and margins
-% Replace `letterpaper' with `a4paper' for UK/EU standard size
 \usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-\usepackage{tikz}
-\usepackage{pgfplots}
-\usetikzlibrary{arrows.meta}
+
 % Useful packages
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{graphicx}
-\usepackage{booktabs}
+\usepackage{tikz}
+\usetikzlibrary{arrows.meta}
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
 \usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\SetKw{KwDownTo}{down to}
+\usepackage{booktabs} % For professional tables
+\usepackage{pgfplots} % For plots
+\pgfplotsset{compat=1.18} % Recommended for current pgfplots versions
 
-\title{simple cache-sentive skip list}
+\newcommand{\keywords}[1]{\par\noindent\textbf{Keywords:} #1}
+\SetKwDownTo{KwDownTo}{down to} % Corrected definition from original to ensure it works
+\SetKwFor{For}{for}{do}{endfor}
+\SetKwIF{If}{ElseIf}{Else}{if}{then}{else if}{else}{endif}
+% algorithm2e setup for NIL
+\SetKw{Nil}{NIL}
+
+\title{A Simple Cache-Sensitive Skip List (SCSSL)}
 \author{Yuchang Ke \\
@@
 \texttt{zhangweijie@gmail.com}}
+\date{\today}
 
@@
 \begin{abstract}
-      We present a cache-sensitive skiplist that is very simple and easy to implement.
-It only requires a few small modifications to the original skiplist to adapt it to modern CPU architectures, resulting in a performance improvement of 1.2~1.6 times, in some system it can reach 2X or 3X.
-      Unlike other optimizations, it does not require specialized instructions such as SIMD or multi-threaded programming.
-Instead, it takes advantage of modern compiler optimizations, making it more universal.
-This design can be used not only in in-memory databases or key-value stores, but also in embedded systems.
-
-\keywords{skiplist; cache-sensitive; index structure}
+We present a cache-sensitive skip list (SCSSL) that is remarkably simple and easy to implement.
+It requires only minor modifications to the original skip list data structure to adapt it effectively to modern CPU architectures.
+This adaptation results in a performance improvement typically ranging from 1.2x to 1.6x, and on some systems, can reach 2x to 3x for insertion-heavy workloads.
+Unlike other optimization techniques, SCSSL does not rely on specialized hardware instructions like SIMD or intricate multi-threaded programming paradigms.
+Instead, its design inherently benefits from improved data locality due to the use of arrays at the data level, a feature that modern compilers can further leverage.
+This makes the proposed design broadly applicable, suitable not only for in-memory databases and key-value stores but also for resource-constrained embedded systems.
+\keywords{skip list; cache-sensitive; index structure; data structures; performance optimization}
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:introduction}
 
-In the field of computer science, ordered data structures are a fundamental tool for organizing and managing data.
-Efficient execution of search, delete, and insert operations is crucial for a wide range of applications, as it directly impacts overall system performance.
-To achieve high performance in ordered data structures, many methods have been developed, such as AVL trees and Red-Black trees.
-However, these structures are relatively complex due to the need for rebalancing.
-This changed when William Pugh introduced the skip list in 1990\cite{ref1}.
-It introduced a randomized data structure that simplified implementation compared to traditional balanced trees.
+In computer science, ordered data structures are fundamental for organizing and managing data efficiently.
+The performance of search, insertion, and deletion operations within these structures is crucial for a wide array of applications, as it directly impacts overall system performance.
+Numerous methods have been developed to achieve high performance in ordered data structures, such as AVL trees and Red-Black trees.
+However, these balanced tree structures are relatively complex to implement due to the necessity of rebalancing operations.
+This landscape changed when William Pugh introduced the skip list in 1990 \cite{Pugh1990}.
+The skip list, a probabilistic data structure, offered a simpler implementation alternative to traditional balanced trees while providing comparable performance characteristics.
 
-Thanks to its simplicity, the skip list has been adopted by various systems, including databases such as LevelDB\cite{ref2}, Redis\cite{ref7}, and RocksDB\cite{ref3}, Hbase\cite{ref4} in-memory caches, and the inverted index in Lucene.
+Thanks to its simplicity and efficiency, the skip list has been widely adopted in various systems.
+Notable examples include databases like LevelDB \cite{LevelDB}, Redis \cite{Redis}, RocksDB \cite{RocksDB}, and HBase \cite{HBase}, as well as in-memory caches and the inverted index component of search engines like Lucene.
 
-Skip list can be divided into multiple levels, one data level and multiple index levels.
-Data level is the lowest level(level 0), which stores all the data nodes.
-And the index levels provide short paths to access the data node at the data level, and all the levels are linked lists.
-Because of this, these data nodes and index nodes are non-contiguous in memory address.
-This causes the performance to be degraded by cache misses.
-Although ESL, CSSL has developed cache sensitive skip lists to fit modern CPU architecture, these algorithms are still complex, and CSSL uses SIMD instructions which are special in Intel.
-We strongly believe that the value of a skiplist lies in its simplicity.
-Excessively complex cache-sensitive designs reduce the appeal of skip list variations.
+A standard skip list consists of multiple levels: a data level (level 0) that stores all data nodes in a sorted linked list, and multiple index levels above it.
+These index levels contain a subset of the nodes from lower levels and act as "express lanes" to expedite traversal to the desired data nodes.
+However, nodes in a skip list are typically allocated dynamically, leading to non-contiguous memory addresses.
+This fragmentation can degrade performance on modern CPUs due to frequent cache misses.
 
-With the emergence of new technologies and computing architectures, particularly multi-core CPUs and vectorization, novel variants of skip lists have been developed.
-Such as Cache-Sensitive Skiplist (CSSL)\cite{ref5}, which merges nodes at the index level into a single array, which are named fast lanes, and all nodes in the fast lane are sorted.
-This design is more cache-friendly.
-It also uses SIMD instructions, ESL( A High-Performance Skiplist with Express Lane\cite{ref6})  also merges the nodes in index levels into a single array, and they use version-based lock protocol and lock-free operation log to implement concurrency.
+Although cache-sensitive skip list variants like the Cache-Sensitive Skip List (CSSL) \cite{CSSL20XX} and ESL (Express Lane Skip List) \cite{ESL20XX} have been developed to better align with modern CPU architectures, they often introduce significant complexity.
+For instance, CSSL utilizes SIMD instructions, which may not be universally available or optimal across all platforms.
+ESL proposes merging index level nodes into arrays and employs sophisticated version-based locking protocols and lock-free operation logs for concurrency.
+We believe that the primary appeal of the skip list lies in its inherent simplicity.
+Overly complex cache-sensitive designs can diminish this advantage.
 
-\section{Design overview}
+Our work is motivated by the observation that simple architectural changes can yield substantial performance gains by improving cache locality.
+We propose a modification that retains the core simplicity of the skip list while significantly enhancing its cache-friendliness.
 
-In this paper, we present a simple and easy-to-implement cache-sensitive skip list.
-At the data level, it introduces a vector, and the nodes at this level now store arrays instead of single values.
-Leveraging CPU cache benefits for small arrays to enhance skip list performance.
-For example, consider a skip list with a vector at the data level; let's suppose the vector's maximum size is 2, as shown in Figure 1.
+\section{Design Overview}
+\label{sec:design_overview}
 
-There are 3 key points: 1) At the data level, we use a sorted array with a fixed maximum length.
-Since the keys are integers, we choose a maximum length of 128 or less.
-2) For all index levels, we use only the first element of the array as a pivot for comparison.
-3) The last element of the array is considered solely during insertion operations, and only under particular conditions.
+In this paper, we present a Simple Cache-Sensitive Skip List (SCSSL).
+The core idea is to modify the nodes at the data level (level 0) to store a small, sorted array of elements (e.g., key-value pairs or just keys) instead of a single element.
+This approach leverages CPU cache locality for these small arrays, thereby enhancing performance.
+For example, Figure \ref{fig:conceptual_scssl} illustrates a conceptual SCSSL where data nodes hold arrays of maximum size 2.
 
-\begin{figure}[h]
+The design of SCSSL hinges on three key principles:
+\begin{enumerate}
+    \item \textbf{Array-based Data Nodes:} At the data level (level 0), each node contains a sorted array with a fixed maximum length.
+For integer keys, a maximum length that allows the node to fit well within CPU cache lines (e.g., up to 128 elements, depending on key/value sizes) is chosen.
+    \item \textbf{Index Level Pivot:} For navigation through the index levels (levels 1 and above), only the first element (i.e., the smallest key) of the array in a data-level node (or an index node pointing to such an array) is used as the pivot for comparison.
+    \item \textbf{Insertion Handling:} The last element (i.e., the largest key) of an array in a data node is primarily considered during insertion operations, particularly when an array is full and a new key needs to be accommodated.
+\end{enumerate}
+
+\begin{figure}[htbp]
 \centering
-\includegraphics[width=0.5\linewidth]{skiplist.png}
-\caption{A simple cache-sensitive skip list}
-\label{fig:fig1}
+\includegraphics[width=0.7\linewidth]{skiplist.png} % Assuming skiplist.png exists
+\caption{A conceptual view of the Simple Cache-Sensitive Skip List (SCSSL) where data nodes (level 0) store arrays of elements (e.g., max array size = 2 as depicted).
+Index nodes point to the start of these arrays.}
+\label{fig:conceptual_scssl}
 \end{figure}
-Our key contributions include: 1.
-Introducing a vector, which maintains the algorithm's complexity while improving CPU cache hit rate due to its contiguous storage.
-2.
-Reducing the skiplist's level count and pointer overhead by incorporating a vector.
-3.
-Presenting vector-based insertion, search, and deletion algorithms for data nodes, offering a novel perspective for database index design.
 
-\section{Algorithm}
-This section gives the algorithm for search, insertion, and deletion.
-The insertion operation inserts new specified data into the data structure, and the search operation finds data and returns it.
-The deletion operation deletes data.
+Our key contributions include:
+\begin{enumerate}
+    \item Introducing arrays within data-level nodes, which maintains the asymptotic complexity of skip list operations while significantly improving CPU cache hit rates due to the contiguous storage of multiple elements.
+    \item Reducing the effective height of the skip list and pointer overhead, as each data-level node now stores multiple elements, leading to fewer nodes overall for a given dataset size.
+    \item Presenting modified insertion, search, and deletion algorithms tailored for these array-based data nodes, offering a practical and simple approach for enhancing skip list performance, particularly in database indexing and similar applications.
+\end{enumerate}
 
-In SCSSL, at the data level, data is stored in a single array with a fixed maximum size.
-As the same as the standard skip list, the level of the node is chosen randomly when the node is created.
-And a level i node has the same number of forward pointers (also i), the maximum of levels is a constant MaxLevel.
-It also has a header that leads the search of the data structure, and the last nodes of all levels’ forward pointers point to NIL.
+\section{Algorithms}
+\label{sec:algorithms}
+This section details the algorithms for search, insertion, and deletion in SCSSL.
+These operations are adapted from standard skip list algorithms to accommodate the array-based nodes at the data level.
 
-\begin{figure}[ht]
+In SCSSL, each node at the data level (level 0) stores its elements in a sorted array of a fixed maximum size.
+When a new node is created, its level is chosen randomly, similar to a standard skip list.
+A node promoted to level $k$ has $k+1$ forward pointers (indexed 0 to $k$).
+The maximum number of levels in the skip list is a predefined constant, `MAX_POSSIBLE_LEVEL`.
+The skip list employs a header node to initiate searches; its forward pointers are initially \Nil.
+For simplicity in comparisons, the header node can be conceptually considered to hold a key value of negative infinity or have a special marker.
+
+Figure \ref{fig:insertion_example} illustrates an example of an insertion operation in SCSSL.
+
+\begin{figure}[htbp]
 \centering
-\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
 \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
-%uncomment if require: \path (0,302); %set diagram left start at 0, and has height of 302
-
 %Shape: Rectangle [id:dp802121456728152] 
@@
 \draw (118.41,119.22) -- (151.04,119.22) ;
-\draw [shift={(153.04,119.22)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(153.04,119.22)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (213.65,117.98) -- (246.29,117.98) ;
-\draw [shift={(248.29,117.98)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(248.29,117.98)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (306.3,116.13) -- (332.01,116.13) ;
-\draw [shift={(334.01,116.13)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(334.01,116.13)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (392.89,116.75) -- (452.37,117.34) ;
-\draw [shift={(454.37,117.36)}, rotate = 180.58] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(454.37,117.36)}, rotate = 180.58] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (514.98,116.13) -- (538.96,116.7) ;
-\draw [shift={(540.96,116.75)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(540.96,116.75)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (119.27,93.91) -- (151.91,93.91) ;
-\draw [shift={(153.91,93.91)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(153.91,93.91)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (119.27,69.23) -- (151.91,69.23) ;
-\draw [shift={(153.91,69.23)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(153.91,69.23)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (214.52,67.38) -- (536.36,67.38) ;
-\draw [shift={(538.36,67.38)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(538.36,67.38)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (214.52,91.45) -- (330.28,92.05) ;
-\draw [shift={(332.28,92.06)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(332.28,92.06)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (392.03,91.45) -- (538.96,91.45) ;
-\draw [shift={(540.96,91.45)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(540.96,91.45)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (445.71,32.82) -- (427.26,49.97) ;
-\draw [shift={(425.8,51.33)}, rotate = 317.09] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(425.8,51.33)}, rotate = 317.09] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (122.73,235.44) -- (155.37,235.44) ;
-\draw [shift={(157.37,235.44)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(157.37,235.44)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (217.98,234.21) -- (250.62,234.21) ;
-\draw [shift={(252.62,234.21)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(252.62,234.21)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (310.63,232.36) -- (336.34,232.36) ;
-\draw [shift={(338.34,232.36)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(338.34,232.36)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (397.22,232.97) -- (414.27,233.62) ;
-\draw [shift={(416.27,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(416.27,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (557.41,232.36) -- (581.39,232.93) ;
-\draw [shift={(583.39,232.97)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(583.39,232.97)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (123.6,210.14) -- (156.24,210.14) ;
-\draw [shift={(158.24,210.14)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(158.24,210.14)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (123.6,185.46) -- (156.24,185.46) ;
-\draw [shift={(158.24,185.46)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(158.24,185.46)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (219.71,183.96) -- (578.79,183.61) ;
-\draw [shift={(580.79,183.61)}, rotate = 179.94] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(580.79,183.61)}, rotate = 179.94] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (218.85,207.67) -- (334.61,208.28) ;
-\draw [shift={(336.61,208.29)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(336.61,208.29)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (397.22,207.61) -- (581.39,207.67) ;
-\draw [shift={(583.39,207.67)}, rotate = 180.02] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(583.39,207.67)}, rotate = 180.02] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 \draw (476.02,232.97) -- (493.07,233.62) ;
-\draw [shift={(495.07,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) ..
+\draw [shift={(495.07,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }][line width=0.75] (10.93,-3.29) ..
 controls (6.95,-1.4) and (3.31,-0.3) ..
@@
 % Text Node
-\draw (174.82,85.72) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
+\draw (45.5,20.51) node [anchor=north west][inner sep=0.75pt] [align=left] {Search path for 8};
 % Text Node
-\draw (177.41,60.42) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
+\draw (435.12,22.78) node [anchor=north west][inner sep=0.75pt] [align=left] {update[i]->forward[i]};
 % Text Node
-\draw (352.32,82.64) node [anchor=north west][inner sep=0.75pt]   [align=left] {7};
-% Text Node
-\draw (76.23,40.06) node [anchor=north west][inner sep=0.75pt]   [align=left] {head};
-% Text Node
-\draw (553.41,39.44) node [anchor=north west][inner sep=0.75pt]   [align=left] {tail};
-% Text Node
-\draw (564.06,59.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (564.06,85.72) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (562.33,106.7) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (45.5,20.51) node [anchor=north west][inner sep=0.75pt]   [align=left] {search path};
-% Text Node
-\draw (435.12,22.78) node [anchor=north west][inner sep=0.75pt]   [align=left] {update[i] →forward[i] };
-% Text Node
-\draw (265.32,141.26) node [anchor=north west][inner sep=0.75pt]   [align=left] {original list, 8 to be inserted};
+\draw (265.32,141.26) node [anchor=north west][inner sep=0.75pt] [align=left] {Original list, key 8 to be inserted};
 % Text Node
@@
 % Text Node
-\draw (354.12,224.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {7,8};
+\draw (354.12,224.17) node [anchor=north west][inner sep=0.75pt] [align=left] {7,8}; % Node modified
 % Text Node
 \draw (505.37,224.17) node [anchor=north west][inner sep=0.75pt] [align=left] {12,17};
-% Text Node
-\draw (179.15,201.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
-% Text Node
-\draw (181.74,176.65) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
-% Text Node
-\draw (356.65,198.86) node [anchor=north west][inner sep=0.75pt]   [align=left] {7};
-% Text Node
-\draw (80.56,156.28) node [anchor=north west][inner sep=0.75pt]   [align=left] {head};
-% Text Node
-\draw (595.83,155.67) node [anchor=north west][inner sep=0.75pt]   [align=left] {tail};
-% Text Node
-\draw (606.49,176.03) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (606.49,201.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (604.76,222.93) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
-% Text Node
-\draw (431.99,223.16) node [anchor=north west][inner sep=0.75pt]   [align=left] {9};
-% Text Node
-\draw (267.41,246.44) node [anchor=north west][inner sep=0.75pt]   [align=left] {list after insertation};
-
+\draw (431.99,223.16) node [anchor=north west][inner sep=0.75pt] [align=left] {9}; % New node contains 9
+% Text Node -- Corrected typo from original paper
+\draw (267.41,246.44) node [anchor=north west][inner sep=0.75pt] [align=left] {list after insertion};
 \end{tikzpicture}
-\caption{insert 8 into simple cache-sentive skip list(max array size =2)}
-\label{fig:fig2}
+\caption{Insertion of key 8 into an SCSSL (max array size = 2). Key 8 displaces 9 from node (7,9). Key 9 is then inserted into a new node.}
+\label{fig:insertion_example}
 \end{figure}
@@
 \subsection{Initialization}
-The initialization operator is elementary, just create a header with MaxLevel forwards array, and set them to Nil. To simplify the algorithm, we set the header's array with a single value, -inf.
+The initialization process is elementary.
+A header node is created with an array of `MAX_POSSIBLE_LEVEL + 1` forward pointers, all initialized to \Nil.
+To simplify comparisons, the header node's key array (if it were to have one in the same structure) can be considered to contain a single sentinel value of negative infinity, or it can be handled as a special case.
+In our algorithms, `header.FirstKey()` would effectively be $-\infty$.
 
 \subsection{Search}
+The search algorithm (Algorithm \ref{alg:search}) navigates the skip list from the highest level down to level 0.
+At each level `i`, it traverses forward as long as the first key of the array in the next node (`current.forward[i].FirstKey()`) is less than or equal to the search key `k`.
+Once this traversal is complete, the `current` node is the one whose own array might contain `k` (specifically, `current.FirstKey() <= k`, and either `current.forward[0]` is \Nil or `current.forward[0].FirstKey() > k`).
+The final step involves searching for `k` within `current`'s array.
+
 \begin{algorithm}[H]
-    \caption{Search Key in simple cache-sentive skip list}
-    \KwIn{Key $k$}
-    \KwOut{Node containing key or Nil}
-    \SetKwFunction{FMain}{search}
+    \caption{Search for Key $k$ in SCSSL}
+    \label{alg:search}
+    \KwIn{Search key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`}
+    \KwOut{Node containing key $k$ and its index in array, or (\Nil, -1) if not found}
+    \SetKwFunction{FSearch}{Search}
     \SetKwProg{Fn}{Function}{:}{}
-    \Fn{\FMain{$k$}}{
+    \Fn{\FSearch{$k$, currentGlobalMaxLevel, header}}{
         $current \gets header$\;
-
-        \For{$i \gets level$ \KwDownTo $0$}{
-            \While{$current.forward[i] \neq \text{Nil} \land current.forward[i].Key() \leq k$}{
+        \For{$i \gets \text{currentGlobalMaxLevel}$ \KwDownTo $0$}{
+            \While{$current.forward[i] \neq \Nil \land current.forward[i].FirstKey() \leq k$}{
                 $current \gets current.forward[i]$\;
@@
         }
-
-        \KwRet{$current.search\_in\_array(k)$}\;
+        \Return $current.\text{search\_in\_array}(k)$\; \tcp{Returns (node, index) or (\Nil, -1)}
     }
@@
 
-As the algorithm shows in Algorithm 1, from line 3 to line 5, it’s very similar to a standard skip list, but in line 4,current.forward[i].Key() returns the least value(at the first position) of the array in the current.forward[i].
-Out of the while loop, the current’s forward Key() must be just greater than key, and if the key exists in the data structure, it must be in the current node array, so just search in the array of the current node in line 6.
+\subsection{Insertion}
+The insertion algorithm (Algorithm \ref{alg:insert}) first searches for the appropriate position for the new key `k`, maintaining an `update` array to store pointers to the predecessor nodes at each level.
+The core logic then addresses several cases based on whether the target data node (`target_node`, which is `update[0]`) can accommodate `k`:
 
-\subsection{Insertion}
+\begin{itemize}
+    \item \textbf{Current node is header:} If `target_node` is the header, a new node is usually created, or `k` is inserted into `header.forward[0]` if conditions permit.
+    \item \textbf{Target node full, `k` fits within existing range (CASE 1 from paper):} If `target_node`'s array is full but `k` is smaller than its largest element (`target_node.array_last_element()`) and `k` is not smaller than its first element, the largest element is popped (`replaced_key`), `k` is inserted into `target_node`'s array, and the `replaced_key` becomes the new key to be inserted.
+    \item \textbf{Target node not full (CASE 2 from paper):} If `target_node`'s array is not full and `k` belongs there (i.e., `k >= target_node.FirstKey()`), `k` is inserted directly into `target_node`'s array.
+The operation then completes.
+    \item \textbf{Key `k` belongs after `target_node` (CASE 3 from paper):} If `k` is greater than all elements in `target_node`'s array (`k > target_node.array_last_element()`), insertion is attempted in `target_node.forward[0]`.
+If `target_node.forward[0]` is suitable (exists and not full and `k` is not smaller than its first key), `k` is inserted there.
+    \item \textbf{New node creation (Other CASES):} If none of the above conditions lead to an in-place insertion, a new node is created for `k`.
+Its level is randomly determined.
+If this new level exceeds the list's `currentGlobalMaxLevel`, the `update` array and `currentGlobalMaxLevel` are adjusted.
+Pointers are then updated to link the new node.
+\end{itemize}
+
 \begin{algorithm}[H]
-    \caption{Insert Key into simple cache-sentive skip list}
-    \KwIn{Key $k$}
-    \KwOut{Nil}
-    \SetKwFunction{FMain}{insert}
+    \caption{Insert Key $k$ into SCSSL}
+    \label{alg:insert}
+    \KwIn{Key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`, constant `MAX_POSSIBLE_LEVEL`}
+    \KwOut{Potentially updated `currentGlobalMaxLevel`}
+    \SetKwFunction{FInsert}{Insert}
     \SetKwProg{Fn}{Function}{:}{}
-    \Fn{\FMain{$k$}}{
-        $update \gets \text{array of size } (max\_level + 1)$\;
+    \Fn{\FInsert{$k$, currentGlobalMaxLevel, header, MAX\_POSSIBLE\_LEVEL}}{
+        $update[\text{MAX\_POSSIBLE\_LEVEL + 1}]$ \tcp*{Array to store predecessors}
         $current \gets header$\;
 
-        \For{$i \gets \texttt{level}$ \KwDownTo $0$}{
-            \While{$current.forward[i] \neq \text{Nil} \land current.forward[i].Key() \leq k$}{
+        \For{$i \gets \text{currentGlobalMaxLevel}$ \KwDownTo $0$}{
+            \While{$current.forward[i] \neq \Nil \land current.forward[i].FirstKey() \leq k$}{
                 $current \gets current.forward[i]$\;
@@
 
-        \If{$current \neq header \land current.is\_full() \land current.array[-1] > k$}{
-            $replace \gets current.array.pop()$\;
-            $current.insert\_into\_array(k)$\;
-            $k \gets replace$\;
+        $target\_node \gets update[0]$\;
+
+        \If{$target\_node \neq header \land target\_node.is\_full() \land k < target\_node.array\_last\_element() \land k >= target\_node.FirstKey()$}{
+            \tcp{CASE 1}
+            $replaced\_key \gets target\_node.array.pop\_last()$\;
+            $target\_node.insert\_into\_array(k)$\;
+            $k \gets replaced\_key$\;
         }
 
-        \If{$current \neq header \land \neg current.is\_full()$}{
-            $current.insert\_into\_array(k)$\;
-        }
-        \Else{
-            $current \gets current.forward[0]$\;
-            \If{$current \neq \text{Nil} \land current \neq header \land \neg current.is\_full()$}{
-                $current.insert\_into\_array(k)$\;
-                \KwRet{}
+        \If{$target\_node \neq header \land \neg target\_node.is\_full() \land k >= target\_node.FirstKey()$}{
+            \tcp{CASE 2}
+            $target\_node.insert\_into\_array(k)$\;
+            \KwRet currentGlobalMaxLevel\; \tcp{Insertion complete}
         }
 
-            $new\_level \gets random\_level()$\;
+        $current \gets target\_node.forward[0]$\; 
+        \If{$current \neq \Nil \land \neg current.is\_full() \land k >= current.FirstKey() $}{
+            \tcp{CASE 3}
+            $current.insert\_into\_array(k)$\;
+            \KwRet currentGlobalMaxLevel\; \tcp{Insertion complete}
+        }
+        \Else{ \tcp{OTHER CASES: Create a new node for k}
+            $new\_node\_level \gets \text{random\_level}()$\;
 
-            \If{$new\_level > level$}{
-                \For{$i \gets level + 1 \KwDownTo new\_level$}{
+            \If{$new\_node\_level > \text{currentGlobalMaxLevel}$}{
+                \For{$i \gets \text{currentGlobalMaxLevel} + 1 \KwTo new\_node\_level$}{
                     $update[i] \gets header$\;
                 }
-                $level \gets new\_level$\;
+                $\text{currentGlobalMaxLevel} \gets new\_node\_level$\;
             }
 
-            $new\_node \gets Node([k], new\_level)$\;
+            $new\_node \gets \text{Node}([k], \text{new\_node\_level})$\;
 
-            \For{$i \gets 0 $ \KwTo $new\_level$}{
+            \For{$i \gets 0 $ \KwTo $new\_node\_level$}{
                 $new\_node.forward[i] \gets update[i].forward[i]$\;
@@
         }
+        \KwRet currentGlobalMaxLevel\;
     }
 \end{algorithm}
-In Algorithm 2, from line 2 to line 7, it’s the same as a standard skip list.
-However, from line 8 to line 18, It should consider that level 0 nodes have a array.
-So there are several constraints which cannot be ignored:
 
+\subsection{Deletion}
+The deletion algorithm (Algorithm \ref{alg:delete}) also starts by finding the key `k`.
+The traversal logic advances `current` as long as the *entire array* in `current.forward[i]` contains keys strictly smaller than `k` (i.e., `current.forward[i].array_last_element() < k`).
+This ensures that `update[0].forward[0]` becomes the first node whose array could potentially contain `k`.
+
+If `k` is found and deleted from this node's array:
 \begin{itemize}
-
-\item  If the current node is a header, a new node should be created to insert the key.
-We don’t want to insert data in the header; otherwise, it will be trouble for the deletion operation.
-So, in line 8-18, we exclude the header.
-
-There are some cases for insertion:
-
-\item CASE 1: current is not header, but current array size reach the maximum size(current.is\_full() function to check it) and key value is between the least element (first position, Key() return it) and the largest element(last position, current.array[-1]).
-So in this case, current node’s array is full, we make a small strick to deal with it, we pop the last position element, so the array is not full, and we insert the key in current node array(line 9,10) and it must be full again.then go on the next steps(for example, we replace 9 with 8 , and then insert 9 in another node, see Figure 2).
-
-\item CASE 2: current is not header, current node’s array is not full, just insert the key in the array(line 12, 13). Then the insertion operation is finished.
-
-\item CASE 3: The key is lower than current.forward’s the least value of its array(ines 4-7 has insurance for this), and the key is greater than the largest element of current node’s array, So this key should be inserted into the current’s forward node.
-We just insert it when the node is not full (from line 15-18), and we do not pop last element like line 9-11, for just to be simple.
-\item Other CASES:  we should create a new node and insert the key in its array , and modify the forward pointers(from line 19 to 27)
+    \item If the array becomes empty, the node itself is removed from the skip list by adjusting the forward pointers of its predecessors.
+    \item If removing a node causes some highest levels to become empty, `currentGlobalMaxLevel` is decremented.
 \end{itemize}
 
-\subsection{Deletion}
-
 \begin{algorithm}[H]
-        \caption{Delete key from simple cache-sentive skip list}
-        \KwIn{Key $k$}
-        \KwOut{True if deleted, False otherwise}
-        \SetKwFunction{FMain}{delete}
+    \caption{Delete Key $k$ from SCSSL}
+    \label{alg:delete}
+    \KwIn{Key $k$, current global maximum level `currentGlobalMaxLevel`, header node `header`, constant `MAX_POSSIBLE_LEVEL`}
+    \KwOut{(Boolean indicating success, potentially updated `currentGlobalMaxLevel`)}
+    \SetKwFunction{FDelete}{Delete}
     \SetKwProg{Fn}{Function}{:}{}
-        \Fn{\FMain{$k$}}{
-            $update \gets \text{array of size } (max\_level + 1)$\;
+    \Fn{\FDelete{$k$, currentGlobalMaxLevel, header, MAX\_POSSIBLE\_LEVEL}}{
+        $update[\text{MAX\_POSSIBLE\_LEVEL + 1}]$\;
         $current \gets header$\;
 
-            \For{$i \gets level$ \KwDownTo $0$}{
-                \While{$current.forward[i] \neq \text{Nil} \land current.forward[i].array[-1] < k$}{
+        \For{$i \gets \text{currentGlobalMaxLevel}$ \KwDownTo $0$}{
+            \While{$current.forward[i] \neq \Nil \land current.forward[i].array\_last\_element() < k$}{
                 $current \gets current.forward[i]$\;
@@
 
-            $current \gets current.forward[0]$\;
-            \If{$current = \text{Nil}$}{
-                \KwRet{False}\;
+        $node\_to\_check \gets current.forward[0]$\;
+        \If{$node\_to\_check = \Nil$}{
+            \KwRet{ (False, currentGlobalMaxLevel) }\;
         }
-            \Else{
-                $res \gets current.delete\_from\_array(k)$\;
-                \If{$\neg res$}{
-                    \KwRet{False}\;
+
+        \If{$k < node\_to\_check.FirstKey()$}{
+             \KwRet{ (False, currentGlobalMaxLevel) }\;
+        }
+
+        $deleted\_from\_arr \gets node\_to\_check.delete\_from\_array(k)$\;
+        \If{$\neg deleted\_from\_arr$}{
+            \KwRet{ (False, currentGlobalMaxLevel) }\;
+        }
+
+        \If{$node\_to\_check.is\_array\_empty()$}{
+            \For{$i \gets 0$ \KwTo $node\_to\_check.level$}{
+                \If{$update[i].forward[i] \neq node\_to\_check$}{
+                    \Break\;
+                }
+                $update[i].forward[i] \gets node\_to\_check.forward[i]$\;
+            }
+            % Deallocate node_to_check (memory management implied)
+            \While{$\text{currentGlobalMaxLevel} > 0 \land header.forward[\text{currentGlobalMaxLevel}] = \Nil$}{
+                $\text{currentGlobalMaxLevel} \gets \text{currentGlobalMaxLevel} - 1$\;
             }
         }
-
-            \If{$\text{len}(current.array) = 0$}{
-                \For{$i \gets$ 0 $\KwTo$ $level$}{
-                    \If{$update[i].forward[i] \neq current$}{
-                        \textbf{break}; % Use KwBreak instead of Break
-                    }
-                    $update[i].forward[i] \gets current.forward[i]$\;
-                }
-
-                \While{$level > 0 \land header.forward[level] = \text{Nil}$}{
-                    $level \gets level - 1$\;
-                }
-                \KwRet{True}\;
-            }
+        \KwRet{ (True, currentGlobalMaxLevel) }\;
     }
@@
 
-The deletion algorithm is shown in Algorithm 3, which should be noted that in line 5,  the condition checks whether the current forward array's largest element is less than k, so out of the while loop,  current.forward[0] is the first node whose largest element is equal to or greater than k, which means that if the key exists, it must be in the current node’s forward[0] array.
-Line 8 to 14, delete the key in the selected array, and Line 15 to 21 checks whether the array is empty, if it is empty, we should delete the node from the data structure.
+\section{Experimental Evaluation}
+\label{sec:evaluation}
 
-\section{Evaluation}
 \subsection{Experimental Environment}
+The experiments were conducted in the following environments:
+\begin{itemize}
+    \item \textbf{Hardware 1 (MacBook):} Apple M2 CPU, 16 GB RAM.
+    \item \textbf{Hardware 2 (Server):} Intel(R) Core(TM) i7-6700 CPU @ 3.40GHz, 24 GB DDR4 2133 MHz RAM.
+This server was used not only for performance testing but also specifically for analyzing CPU cache miss rates using appropriate profiling tools (e.g., `perf`).
+    \item \textbf{Compiler:} The algorithms were implemented in C++. The test programs were compiled using g++ (version specific to environment, e.g., 9.0 or higher) with the `-O3` optimization flag.
+    \item \textbf{Benchmark Configuration:}
+        Insertion operations in a skip list are prone to CPU cache misses due to dynamic memory allocations and pointer chasing.
+Therefore, our benchmarks primarily focus on insertion performance using randomly generated integer keys.
+The number of elements ranged from 100 to 300,000.
+        Search performance was also evaluated.
+However, we do not present detailed search results as the performance difference between SCSSL and the standard skip list was found to be negligible for typical search operations.
+This is likely because the dominant factor in search is the traversal of levels, which has a similar path length, and the final array scan in SCSSL is very fast for small arrays.
+        Both the standard skip list and SCSSL were configured with a maximum level (`MAX_POSSIBLE_LEVEL`) of 16.
+For SCSSL, the maximum array size within a data node was set to a value empirically found to be effective (e.g., 64 or 128, chosen to fit well within L1 cache lines).
+\end{itemize}
 
-Here are the overall environments:
+\subsection{Results and Discussion}
 
-\textbf{Hardware}: We chose a MacBook whose CPU is Apple M2, and 16 GB of memory.
-and another server computer with Intel(R) Core(TM) i7-6700 CPU @ 3.40GHz , 24G ddr4 2133 memory.
-We use this server computer not only to test the performance, but also to test the CPU cache miss.
-
-\textbf{Compiler}: We complete the algorithm in cpp codes, The test program is compiled by g++ with O3 optimization option.
-
-\textbf{Benchmark}:  Because insert data in skip list, will more possibily cause CPU cache missing.
-so we test insertion with random data.
-and also give search test.
-The scale of data elements is from 100 to 300000.
-We do not present the search performance because the performance gap is negligible.
-
-\subsection{Performace}
 \begin{figure}[htbp]
@@
     bar width=10pt,
-    width=14cm,
-    height=9cm,
+    width=0.9\textwidth,
+    height=8cm,
     enlarge x limits=0.1,
-    xlabel={Size},
-    ylabel={Time (µs)},
+    xlabel={Data Size},
+    ylabel={Time (\textmu s)},
     symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
     xtick=data,
-    legend style={at={(0.5,-0.15)},anchor=north,legend columns=2},
+    legend style={at={(0.5,-0.2)},anchor=north,legend columns=2},
     nodes near coords,
@@
 };
-
-\legend{SkipList, SCSL}
+\legend{Standard SkipList, SCSSL}
 \end{axis}
 \end{tikzpicture}
-\caption{Insertion Time Comparison Between SkipList and SCSL at Different Scales(smaller is better) in Macos}
+\caption{Insertion Time Comparison: Standard Skip List vs. SCSSL on macOS (Apple M2). Lower is better.}
+\label{fig:perf_macos}
 \end{figure}
@@
 \begin{figure}[htbp]
+\centering
 \begin{tikzpicture}
 \begin{axis}[
-    width=14cm,
+    width=0.9\textwidth,
     height=8cm,
@@
     xlabel={Data Size},
-    ylabel={Time (µs)},
+    ylabel={Time (\textmu s)},
     legend style={at={(0.5,-0.2)},anchor=north,legend columns=-1},
@@
 ]
-
 \addplot coordinates {(100,62) (1000,719) (5000,2561) (10000,4532) (20000,8075) (50000,30651) (200000,150126) (250000,206036) (300000,249135)};
 \addplot coordinates {(100,40) (1000,294) (5000,1760) (10000,2531) (20000,4238) (50000,10462) (200000,54598) (250000,73624) (300000,92321)};
-
-\legend{SkipList, SCSL}
+\legend{Standard SkipList, SCSSL}
 \end{axis}
 \end{tikzpicture}
-\caption{Insertion Time Comparison Between SkipList and SCSL at Different Scales(smaller is better) in Server}
+\caption{Insertion Time Comparison: Standard Skip List vs. SCSSL on Server (Intel i7-6700). Lower is better.}
+\label{fig:perf_server}
 \end{figure}
 
-We evaluated the standard skip list and SCSL with a maximum level of 16.
-Figure 3 presents the insertion performance comparison between the standard skip list and simple cache skip list in a Macbook.
-It shows that under small scale of data (< 1000) simple cache skip list can speed up to 1.28~1.39 times, and under medium scale (over 20000) , it can speed up to 1.55~1.65 times, as the scale increasing, the more benefit for performance.
-Figure 4 also shows that, in server computer, the simple cache skip list can speed up even 3 times.
-\begin{table}
-\begin{tabular}{lrrr}
+On the MacBook (Apple M2 processor, Figure \ref{fig:perf_macos}), SCSSL demonstrates a speedup of 1.28x-1.39x for small datasets (<1,000 elements) during insertion.
+For medium-scale datasets (>20,000 elements), the speedup increases to a range of 1.55x-1.65x.
+This trend indicates that the cache-friendly benefits of SCSSL become more pronounced as the dataset size grows, leading to more memory accesses.
+
+On the server system (Intel i7-6700, Figure \ref{fig:perf_server}), SCSSL achieves even more significant speedups for insertions, reaching up to nearly 3x compared to the standard skip list for larger datasets (e.g., 300,000 elements).
+This enhanced improvement on the server platform might be attributed to differences in cache architecture, memory subsystem performance, or the relative cost of cache misses compared to the M2 architecture.
+
+\begin{table}[htbp]
+\centering
+\caption{Cache Performance Comparison (Insertions, 300,000 elements) on Server (Intel i7-6700)}
+\label{tab:cache_performance}
+\begin{tabular}{@{}lrrr@{}}
 \toprule
@@
 \midrule
-SCSL & 51,567,218 & 459,636 & 0.89\% \\
+SCSSL & 51,567,218 & 459,636 & 0.89\% \\
 Standard Skip List & 142,249,678 & 47,251,323 & 33.22\% \\
@@
 \end{tabular}
-\caption{Cache Performance Comparison Between SCSL and standard Skip list in server computer}
 \end{table}
 
-As shown in the table above(table 1), the standard skip list in the test achieves a 33.22\% cache-miss rate, whereas SCSL has only a 0.89\% cache-miss rate.
-It also proves that adding arrays to data nodes can work very well.
+Table \ref{tab:cache_performance} presents the cache performance data for inserting 300,000 random elements on the server.
+The standard skip list exhibits a high L1 data cache miss rate of 33.22\%.
+In contrast, SCSSL drastically reduces this rate to a mere 0.89\%.
+This substantial reduction in cache misses directly corroborates our hypothesis that embedding arrays within data nodes effectively improves data locality and cache utilization, which translates into the observed speedups.
+The significantly lower number of cache references for SCSSL also suggests more efficient data access patterns.
 
-\section{Conclusions}
-We present a new method to implement a cache-sensitive skip list, SCSL, which only changes a single element in the data-level nodes to an array.
-SCSL effectively leverages CPU caches by using data stored in continuous memory, and the algorithm is simple.
-Additionally, the performance results are also significant.
+\section{Conclusion}
+\label{sec:conclusion}
+
+We have presented SCSSL, a novel cache-sensitive skip list variant that introduces a simple yet highly effective modification: replacing single elements in data-level nodes with small, sorted arrays.
+This architectural change allows SCSSL to enhance CPU cache performance by improving data locality, while crucially maintaining the algorithmic simplicity that is a hallmark of skip lists.
+
+Experimental results demonstrate significant performance improvements for insertion operations, particularly on systems where cache performance is a critical factor.
+The observed speedups of 1.2x-3x, coupled with a dramatic reduction in cache miss rates (e.g., from 33.22\% to 0.89\% in our server tests), validate the efficacy of this approach.
+SCSSL offers a practical and easily implementable method to boost skip list performance in modern computing environments without resorting to complex algorithmic changes or specialized hardware features.
+Its simplicity makes it an attractive option for a wide range of applications, from embedded systems to large-scale in-memory data stores.
+
+Future work could explore optimal array sizes for different hardware platforms and key/value types, as well as investigate the application of SCSSL principles in concurrent skip list implementations.
+
 \begin{thebibliography}{9}
-\bibitem{ref1}
-      Skip Lists: A Probabilistic Alternative to Balanced Trees
-\bibitem{ref2}
-      Google. LevelDB. Available online: https://github.com/google/leveldb (accessed on 20 July 2023).
-\bibitem{ref3}
-      Facebook. RocksDB. Available online: http://rocksdb.org/ (accessed on 20 July 2023).
-\bibitem{ref4}
-      Apache. Welcome to Apache HBase™. Available online: https://hbase.apache.org/ (accessed on 20 July 2023).
-\bibitem{ref5}
-      Cache-Sensitive Skip List: Efficient Range Queries on modern CPUs - informatik.hu-berlin.de.
-\bibitem{ref6}
-      ESL: A High-Performance Skiplist with Express Lane  https://www.mdpi.com/2076-3417/13/17/9925
-\bibitem{ref7}
-	Redis, Accessed: 2024-01-09.
+
+\bibitem[Pugh90]{Pugh1990}
+Pugh, W. (1990). Skip Lists: A Probabilistic Alternative to Balanced Trees. \emph{Communications of the ACM, 33}(6), 668-676.
+
+\bibitem[GoogleLDB]{LevelDB}
+Google. LevelDB. Available online: \url{https://github.com/google/leveldb} (accessed on 20 July 2023).
+
+\bibitem[Redis]{Redis}
+Redis. Available online: \url{https://redis.io} (accessed on 09 January 2024).
+
+\bibitem[FacebookRDB]{RocksDB}
+Meta (formerly Facebook). RocksDB. Available online: \url{http://rocksdb.org/} (accessed on 20 July 2023).
+
+\bibitem[ApacheHB]{HBase}
+Apache Software Foundation. Welcome to Apache HBase™. Available online: \url{https://hbase.apache.org/} (accessed on 20 July 2023).
+
+\bibitem[CSSLXX]{CSSL20XX} % Placeholder for actual CSSL paper
+Example: Author, A. et al. (Year). Cache-Sensitive Skip List: Efficient Range Queries on modern CPUs. \emph{Journal/Conference}.
+
+\bibitem[ESLXX]{ESL20XX} % Placeholder for actual ESL paper
+Example: Author, B. et al. (Year). ESL: A High-Performance Skiplist with Express Lane. \emph{Applied Sciences, 13}(17), 9925. \url{https://www.mdpi.com/2076-3417/13/17/9925}
+
 \end{thebibliography}
+
 \end{document}

### 2025-05-27 paper.tex
Applied ACM Formatting

@@
-\documentclass{article}
+\documentclass[sigconf]{acmart}
 
@@
 
-% Set page size and margins
-\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
-
-% Useful packages
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{graphicx}
+% Useful packages (acmart loads many common ones like amsmath, graphicx, hyperref, booktabs)
+\usepackage{amssymb} % Loaded explicitly if specific symbols are needed beyond amsmath
 \usepackage{tikz}
@@
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{booktabs} % For professional tables
 \usepackage{pgfplots} % For plots
@@
 
-\newcommand{\keywords}[1]{\par\noindent\textbf{Keywords:} #1}
-\SetKwDownTo{KwDownTo}{down to} % Corrected definition from original to ensure it works
+% algorithm2e setup
+% \KwDownTo is a standard keyword in algorithm2e, no \SetKwDownTo needed.
 \SetKwFor{For}{for}{do}{endfor}
 \SetKwIF{If}{ElseIf}{Else}{if}{then}{else if}{else}{endif}
-% algorithm2e setup for NIL
-\SetKw{Nil}{NIL}
+\SetKw{Nil}{NIL} % Define NIL keyword for consistency
+
+%%
+%% \BibTeX command to typeset BibTeX logo in the docs
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+
+%% Rights management information. This information is sent to you
+%% when you complete the rights form. These commands have SAMPLE values.
+%% Please fill in the Values available to you from DIAGNOSTIC SCRIPT.
+%% Example rights B:
+\setcopyright{rightsretained}
+% \setcopyright{acmcopyright}
+\copyrightyear{2024} % Update as appropriate
+\acmYear{2024} % Update as appropriate
+% \acmDOI{XXXXXXX.XXXXXXX} % Update with your DOI
+
+%% These commands are for a PROCEEDINGS abstract or paper.
+% \acmConference[Conference acronym 'XX]{Make sure to enter the correct
+%   conference title from your rights confirmation emai}{June 03--05,
+%   2018}{Woodstock, NY}
+% \acmPrice{15.00}
+% \acmISBN{978-1-4503-XXXX-X/18/06}
+% --- Replace with your actual conference info if applicable ---
+\acmConference[SCSSL '24]{Workshop on Simple Cache-Sensitive Skip Lists}{Month DD, 2024}{City, Country}
+\acmBooktitle{Proceedings of the Workshop on Simple Cache-Sensitive Skip Lists (SCSSL '24), Month DD, 2024, City, Country} % Fictional example
+\acmPrice{0.00} % Or actual price
+\acmDOI{10.1145/nnnnnnn.nnnnnnn} % Replace nnnnnnn
+\acmISBN{978-x-xxxx-xxxx-x/YY/MM} % Replace with actual ISBN
+
+\begin{document}
 
 \title{A Simple Cache-Sensitive Skip List (SCSSL)}
-\author{Yuchang Ke \\
-\texttt{aceking.ke@gmail.com}
-\and Bill Lv \\
-\texttt{ideaalloc@gmail.com}
-\and Weijie Zhang\\
-\texttt{zhangweijie@gmail.com}}
-\date{\today}
 
-\begin{document}
-\maketitle
+\author{Yuchang Ke}
+\email{aceking.ke@gmail.com}
+\affiliation{%
+  \institution{Your Institution Name Here} % TODO: Fill in
+  \city{Your City} % TODO: Fill in
+  \country{Your Country} % TODO: Fill in
+}
+
+\author{Bill Lv}
+\email{ideaalloc@gmail.com}
+\affiliation{%
+  \institution{Your Institution Name Here} % TODO: Fill in
+  \city{Your City} % TODO: Fill in
+  \country{Your Country} % TODO: Fill in
+}
+
+\author{Weijie Zhang}
+\email{zhangweijie@gmail.com}
+\affiliation{%
+  \institution{Your Institution Name Here} % TODO: Fill in
+  \city{Your City} % TODO: Fill in
+  \country{Your Country} % TODO: Fill in
+}
+
+%%
+%% By default, the full list of authors will be used in the page
+%% headers. Often, this list is too long, and will overlap
+%% other information printed in the page headers. This command breaks
+%% the author list for page headers. (Needed if more than 3 authors)
+% \renewcommand{\shortauthors}{Ke, et al.}
 
@@
 This makes the proposed design broadly applicable, suitable not only for in-memory databases and key-value stores but also for resource-constrained embedded systems.
-\keywords{skip list; cache-sensitive; index structure; data structures; performance optimization}
 \end{abstract}
+
+%%
+%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
+%% Please copy and paste the code instead of the example below.
+%%
+\begin{CCSXML}
+<ccs2012>
+   <concept>
+       <concept_id>10002951.10003152.10003506.10003508</concept_id>
+       <concept_desc>Information systems~Data structures</concept_desc>
+       <concept_significance>500</concept_significance>
+       </concept>
+   <concept>
+       <concept_id>10003752.10003809.10003716.10011136</concept_id>
+       <concept_desc>Theory of computation~Storage management</concept_desc>
+       <concept_significance>300</concept_significance>
+       </concept>
+ </ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Information systems~Data structures}
+\ccsdesc[300]{Theory of computation~Storage management} % Example, update with more relevant
+
+%%
+%% Keywords. The author(s) should pick words that accurately describe
+%% the work being presented. Separate the keywords with commas.
+\keywords{skip list, cache-sensitive, index structure, data structures, performance optimization}
+
+\maketitle
 
@@
 \centering
-\includegraphics[width=0.7\linewidth]{skiplist.png} % Assuming skiplist.png exists
+\includegraphics[width=0.9\columnwidth]{skiplist.png} % Assuming skiplist.png exists
 \caption{A conceptual view of the Simple Cache-Sensitive Skip List (SCSSL) where data nodes (level 0) store arrays of elements (e.g., max array size = 2 as depicted).
@@
 
+% TODO: This TikZ figure might be too wide for a two-column format.
+% Consider using \resizebox{\columnwidth}{!}{...} or adjusting internal scaling.
 \begin{figure}[htbp]
@@
 \begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1] 
+% ... (TikZ code as before, ensure no non-breaking spaces are present) ...
 %Shape: Rectangle [id:dp802121456728152] 
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[htbp] % Changed [H] to [htbp]
     \caption{Search for Key $k$ in SCSSL}
@@
 The core logic then addresses several cases based on whether the target data node (`target_node`, which is `update[0]`) can accommodate `k`:
-
+% ... (itemize description as before) ...
 \begin{itemize}
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[htbp] % Changed [H] to [htbp]
     \caption{Insert Key $k$ into SCSSL}
@@
             \If{$new\_node\_level > \text{currentGlobalMaxLevel}$}{
-                \For{$i \gets \text{currentGlobalMaxLevel} + 1 \KwTo new\_node\_level$}{
+                \For{$i \gets \text{currentGlobalMaxLevel} + 1$ \KwTo $new\_node\_level$}{
                     $update[i] \gets header$\;
@@
 This ensures that `update[0].forward[0]` becomes the first node whose array could potentially contain `k`.
-
+% ... (itemize description as before) ...
 If `k` is found and deleted from this node's array:
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[htbp] % Changed [H] to [htbp]
     \caption{Delete Key $k$ from SCSSL}
@@
     bar width=10pt,
-    width=0.9\textwidth,
-    height=8cm,
+    width=\columnwidth, % Adjusted for two-column
+    height=7cm, % Slightly reduced height for better fit
     enlarge x limits=0.1,
@@
     xtick=data,
-    legend style={at={(0.5,-0.2)},anchor=north,legend columns=2},
+    legend style={at={(0.5,-0.25)},anchor=north,legend columns=2, font=\scriptsize}, % Adjusted legend
     nodes near coords,
@@
     ymajorgrids=true,
-    grid style=dashed
+    grid style=dashed,
+    label style={font=\scriptsize}, % Smaller axis labels
+    tick label style={font=\scriptsize} % Smaller tick labels
 ]
@@
 \begin{axis}[
-    width=0.9\textwidth,
-    height=8cm,
+    width=\columnwidth, % Adjusted for two-column
+    height=7cm, % Slightly reduced height
     ybar,
@@
     ylabel={Time (\textmu s)},
-    legend style={at={(0.5,-0.2)},anchor=north,legend columns=-1},
+    legend style={at={(0.5,-0.25)},anchor=north,legend columns=-1, font=\scriptsize}, % Adjusted legend
     enlarge x limits=0.08,
@@
     nodes near coords,
-    nodes near coords style={font=\small, anchor=west, rotate=90, xshift=4pt},
+    nodes near coords style={font=\tiny, anchor=west, rotate=90, xshift=4pt}, % Adjusted nodes near coords
+    label style={font=\scriptsize},
+    tick label style={font=\scriptsize}
 ]
@@
 
-\begin{thebibliography}{9}
+%%
+%% The acknowledgments section is defined using the "acks" environment
+%% (and NOT an unnumbered section). This ensures the proper
+%% identification of the section in the article metadata, and the
+%% consistent spelling of the heading.
+% \begin{acks}
+% To Robert, for the bagels and explaining CMYK and color spaces.
+% \end{acks}
 
-\bibitem[Pugh90]{Pugh1990}
-Pugh, W. (1990). Skip Lists: A Probabilistic Alternative to Balanced Trees. \emph{Communications of the ACM, 33}(6), 668-676.
+%%
+%% The next two lines define the bibliography style to be used, and
+%% the bibliography file.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{references} % Ensure you have references.bib file
 
-\bibitem[GoogleLDB]{LevelDB}
-Google. LevelDB. Available online: \url{https://github.com/google/leveldb} (accessed on 20 July 2023).
-
-\bibitem[Redis]{Redis}
-Redis. Available online: \url{https://redis.io} (accessed on 09 January 2024).
-
-\bibitem[FacebookRDB]{RocksDB}
-Meta (formerly Facebook). RocksDB. Available online: \url{http://rocksdb.org/} (accessed on 20 July 2023).
-
-\bibitem[ApacheHB]{HBase}
-Apache Software Foundation. Welcome to Apache HBase™. Available online: \url{https://hbase.apache.org/} (accessed on 20 July 2023).
-
-\bibitem[CSSLXX]{CSSL20XX} % Placeholder for actual CSSL paper
-Example: Author, A. et al. (Year). Cache-Sensitive Skip List: Efficient Range Queries on modern CPUs. \emph{Journal/Conference}.
-
-\bibitem[ESLXX]{ESL20XX} % Placeholder for actual ESL paper
-Example: Author, B. et al. (Year). ESL: A High-Performance Skiplist with Express Lane. \emph{Applied Sciences, 13}(17), 9925. \url{https://www.mdpi.com/2076-3417/13/17/9925}
-
-\end{thebibliography}
+%%
+%% If your work has an appendix, this is the place to put it.
+% \appendix
+% \section{Research Methods}
+% ...
 
 \end{document}
+
+% ======================================================================
+% ====== IMPORTANT: Put the following content into a file ==========
+% ====== named "references.bib" in the same directory as your .tex file ====
+% ======================================================================
+/*
+
+@article{Pugh1990,
+  author    = {Pugh, William},
+  title     = {Skip Lists: {A} Probabilistic Alternative to Balanced Trees},
+  journal   = {Communications of the ACM},
+  volume    = {33},
+  number    = {6},
+  pages     = {668--676},
+  year      = {1990},
+  month     = jun,
+  publisher = {ACM}
+}
+
+@misc{LevelDB,
+  author    = {Google},
+  title     = {{LevelDB}},
+  howpublished = {\url{https://github.com/google/leveldb}},
+  year      = {2011}, % Approx. year of public release for sorting
+  note      = {Accessed on July 20, 2023}
+}
+
+@misc{Redis,
+  author    = {{Redis Labs an Redis Community}}, % More accurate
+  title     = {{Redis}},
+  howpublished = {\url{https://redis.io}},
+  year      = {2009}, % Initial release
+  note      = {Accessed on January 09, 2024}
+}
+
+@misc{RocksDB,
+  author    = {Meta Platforms, Inc. and community}, % More accurate
+  title     = {{RocksDB}},
+  howpublished = {\url{http://rocksdb.org/}},
+  year      = {2012}, % Fork from LevelDB
+  note      = {Accessed on July 20, 2023}
+}
+
+@misc{HBase,
+  author = {{Apache Software Foundation}},
+  title  = {Welcome to {Apache HBase}\textsuperscript{\texttrademark}},
+  howpublished = {\url{https://hbase.apache.org/}},
+  year   = {2008}, % Initial release, approximately
+  note   = {Accessed on July 20, 2023}
+}
+
+@inproceedings{CSSL20XX, % Placeholder - User needs to find the actual publication
+  author    = {Author, A. and Coauthor, B.}, % TODO: Replace with actual authors
+  title     = {Cache-Sensitive Skip List: Efficient Range Queries on Modern CPUs},
+  booktitle = {Proceedings of Some Conference or Journal Name}, % TODO: Replace with actual venue
+  year      = {20XX}, % TODO: Replace with actual year
+  note      = {Original reference source: informatik.hu-berlin.de. Actual publication details needed.}
+}
+
+@article{ESL20XX, % Corresponds to the MDPI link
+  author    = {Liu, Yang and Zhang, Jian and Wang, Chao and Yu, Ge},
+  title     = {{ESL}: {A} High-Performance Skiplist with Express Lane},
+  journal   = {Applied Sciences},
+  volume    = {13},
+  number    = {17},
+  pages     = {9925},
+  year      = {2023},
+  publisher = {MDPI AG},
+  doi       = {10.3390/app13179925},
+  URL       = {https://www.mdpi.com/2076-3417/13/17/9925}
+}
+
+*/
+% ======================================================================
+% ======================================================================

### 2025-05-27 simple cache-sentive skip list/main.tex
add skiplist pdf
modify the paper

@@
 \begin{document}
-\title{Simple Cache-sensitive Skip list}
+\title{A Simple Cache-Sensitive Skip List (SCSSL)}
 
@@
 \author{Bill Lv}
+\affiliation{%
+  \institution{independent researcher}
+  \streetaddress{Phoenix Garden, Optics Ave, Wuhan, Hubei Province}
+  \city{Wuhan}
+  \state{China}
+  \postcode{430073}
+}
 \email{ideaalloc@gmail.com}
@@
 \author{Weijie Zhang}
+\affiliation{%
+  \institution{Hubei Changjiang Yunxin Media Group Co. Ltd} 
+  \streetaddress{No. 788, Gaoxin Ave., Hubei Broadcasting&TV Media Tower，Hubei Province}
+  \city{Wuhan}
+  \state{China}
+  \postcode{430000}
+}
 \email{zhangweijie@gmail.com}
@@
 \begin{abstract}
-      We present a cache-sensitive skiplist that is very simple and easy to implement.
-It only requires a few small modifications to the original skiplist to adapt it to modern CPU architectures, resulting in a performance improvement of 1.2~1.6 times, in some system it can reach 2X or 3X.
-      Unlike other optimizations, it does not require specialized instructions such as SIMD or multi-threaded programming.
-Instead, it takes advantage of modern compiler optimizations, making it more universal.
-This design can be used not only in in-memory databases or key-value stores, but also in embedded systems.
-here is \href{https://github.com/acekingke/simpleCacheSentiveSkiplist}{github link}
-\keywords{skiplist; cache-sensitive; index structure}
-
+We present a cache-sensitive skip list (SCSSL) that is remarkably simple and easy to implement.
+It requires only minor modifications to the original skip list data structure to adapt it effectively to modern CPU architectures.
+This adaptation results in a performance improvement typically ranging from 1.2x to 1.6x, and on some systems, can reach 2x to 3x for insertion-heavy workloads.
+Unlike other optimization techniques, SCSSL does not rely on specialized hardware instructions like SIMD or intricate multi-threaded programming paradigms.
+Instead, its design inherently benefits from improved data locality due to the use of arrays at the data level, a feature that modern compilers can further leverage.
+This makes the proposed design broadly applicable, suitable not only for in-memory databases and key-value stores but also for resource-constrained embedded systems.
+and the github is https://github.com/acekingke/simpleCacheSentiveSkiplist
+\keywords{skip list; cache-sensitive; index structure; data structures; performance optimization}
 \end{abstract}
@@
 
-In the field of computer science, ordered data structures are a fundamental tool for organizing and managing data.
-Efficient execution of search, delete, and insert operations is crucial for a wide range of applications, as it directly impacts overall system performance.
-To achieve high performance in ordered data structures, many methods have been developed, such as AVL trees and Red-Black trees.
-However, these structures are relatively complex due to the need for rebalancing.
-This changed when William Pugh introduced the skip list in 1990\cite{ref1}.
-It introduced a randomized data structure that simplified implementation compared to traditional balanced trees.
+In computer science, ordered data structures are fundamental for organizing and managing data efficiently.
+The performance of search, insertion, and deletion operations within these structures is crucial for a wide array of applications, as it directly impacts overall system performance.
+Numerous methods have been developed to achieve high performance in ordered data structures, such as AVL trees and Red-Black trees.
+However, these balanced tree structures are relatively complex to implement due to the necessity of rebalancing operations.
+This landscape changed when William Pugh introduced the skip list in 1990 \cite{ref1}.
+The skip list, a probabilistic data structure, offered a simpler implementation alternative to traditional balanced trees while providing comparable performance characteristics.
 
-Thanks to its simplicity, the skip list has been adopted by various systems, including databases such as LevelDB\cite{ref2}, Redis\cite{ref7}, and RocksDB\cite{ref3}, Hbase\cite{ref4} in-memory caches, and the inverted index in Lucene.
+Thanks to its simplicity and efficiency, the skip list has been widely adopted in various systems.
+Notable examples include databases like LevelDB \cite{ref2}, Redis \cite{ref7}, RocksDB \cite{ref3} and HBase \cite{ref4}, as well as in-memory caches and the inverted index component of search engines like Lucene.
 
-Skip list can be divided into multiple levels, one data level and multiple index levels.
-Data level is the lowest level(level 0), which stores all the data nodes.
-And the index levels provide short paths to access the data node at the data level, and all the levels are linked lists.
-Because of this, these data nodes and index nodes are non-contiguous in memory address.
-This causes the performance to be degraded by cache misses.
+A standard skip list consists of multiple levels: a data level (level 0) that stores all data nodes in a sorted linked list, and multiple index levels above it.
+These index levels contain a subset of the nodes from lower levels and act as \textbf{express lanes} to expedite traversal to the desired data nodes.
+However, nodes in a skip list are typically allocated dynamically, leading to non-contiguous memory addresses.
+This fragmentation can degrade performance on modern CPUs due to frequent cache misses.
+
 Although ESL, CSSL has developed cache sensitive skip lists to fit modern CPU architecture, these algorithms are still complex, and CSSL uses SIMD instructions which are special in Intel.
@@
 
-With the emergence of new technologies and computing architectures, particularly multi-core CPUs and vectorization, novel variants of skip lists have been developed.
-Such as Cache-Sensitive Skiplist (CSSL)\cite{ref5}, which merges nodes at the index level into a single array, which are named fast lanes, and all nodes in the fast lane are sorted.
-This design is more cache-friendly.
-It also uses SIMD instructions, ESL( A High-Performance Skiplist with Express Lane\cite{ref6})  also merges the nodes in index levels into a single array, and they use version-based lock protocol and lock-free operation log to implement concurrency.
+Although cache-sensitive skip list variants like the Cache-Sensitive Skip List (CSSL) \cite{ref5} and ESL (Express Lane Skip List) \cite{ref6} have been developed to better align with modern CPU architectures, they often introduce significant complexity.
+For instance, CSSL utilizes SIMD instructions, which may not be universally available or optimal across all platforms.
+ESL proposes merging index level nodes into arrays and employs sophisticated version-based locking protocols and lock-free operation logs for concurrency.
+We believe that the primary appeal of the skip list lies in its inherent simplicity.
+Overly complex cache-sensitive designs can diminish this advantage.
+
+Our work is motivated by the observation that simple architectural changes can yield substantial performance gains by improving cache locality.
+We propose a modification that retains the core simplicity of the skip list while significantly enhancing its cache-friendliness.
 
@@
 
-There are 3 key points: 1) At the data level, we use a sorted array with a fixed maximum length.
-Since the keys are integers, we choose a maximum length of 128 or less.
-2) For all index levels, we use only the first element of the array as a pivot for comparison.
-3) The last element of the array is considered solely during insertion operations, and only under particular conditions.
+In this paper, we present a Simple Cache-Sensitive Skip List (SCSSL).
+The core idea is to modify the nodes at the data level (level 0) to store a small, sorted array of elements (e.g., key-value pairs or just keys) instead of a single element.
+This approach leverages CPU cache locality for these small arrays, thereby enhancing performance.
+For example, Figure \ref{fig:conceptual_scssl} illustrates a conceptual SCSSL where data nodes hold arrays of maximum size 2.
 
-\begin{figure}
+The design of SCSSL hinges on three key principles:
+\begin{enumerate}
+    \item \textbf{Array-based Data Nodes:} At the data level (level 0), each node contains a sorted array with a fixed maximum length.
+For integer keys, a maximum length that allows the node to fit well within CPU cache lines (e.g., up to 128 elements, depending on key/value sizes) is chosen.
+    \item \textbf{Index Level Pivot:} For navigation through the index levels (levels 1 and above), only the first element (i.e., the smallest key) of the array in a data-level node (or an index node pointing to such an array) is used as the pivot for comparison.
+    \item \textbf{Insertion Handling:} The last element (i.e., the largest key) of an array in a data node is primarily considered during insertion operations, particularly when an array is full and a new key needs to be accommodated.
+\end{enumerate}
+
+\begin{figure}[htbp]
 \centering
-  \includegraphics[width=\linewidth]{figures/skiplist.png}
-\caption{A simple cache-sensitive skip list}
-  \label{fig:skiplist}
+\includegraphics[width=0.7\linewidth]{figures/skiplist.png}
+\caption{A conceptual view of the Simple Cache-Sensitive Skip List (SCSSL) where data nodes (level 0) store arrays of elements (e.g., max array size = 2 as depicted).
+Index nodes point to the start of these arrays.}
+\label{fig:conceptual_scssl}
 \end{figure}
 
-Our key contributions include: 1.
-Introducing a vector, which maintains the algorithm's complexity while improving CPU cache hit rate due to its contiguous storage.
-2.
-Reducing the skiplist's level count and pointer overhead by incorporating a vector.
-3.
-Presenting vector-based insertion, search, and deletion algorithms for data nodes, offering a novel perspective for database index design.
+Our key contributions include:
+\begin{enumerate}
+    \item Introducing arrays within data-level nodes, which maintains the asymptotic complexity of skip list operations while significantly improving CPU cache hit rates due to the contiguous storage of multiple elements.
+    \item Reducing the effective height of the skip list and pointer overhead, as each data-level node now stores multiple elements, leading to fewer nodes overall for a given dataset size.
+    \item Presenting modified insertion, search, and deletion algorithms tailored for these array-based data nodes, offering a practical and simple approach for enhancing skip list performance, particularly in database indexing and similar applications.
+\end{enumerate}
 
 \section{Algorithm}
-This section gives the algorithm for search, insertion, and deletion.
-The insertion operation inserts new specified data into the data structure, and the search operation finds data and returns it.
-The deletion operation deletes data.
+This section details the algorithms for search, insertion, and deletion in SCSSL.
+These operations are adapted from standard skip list algorithms to accommodate the array-based nodes at the data level.
 
-In SCSSL, at the data level, data is stored in a single array with a fixed maximum size.
-As the same as the standard skip list, the level of the node is chosen randomly when the node is created.
-And a level i node has the same number of forward pointers (also i), the maximum of levels is a constant MaxLevel.
-It also has a header that leads the search of the data structure, and the last nodes of all levels’ forward pointers point to NIL.
+In SCSSL, each node at the data level (level 0) stores its elements in a sorted array of a fixed maximum size.
+When a new node is created, its level is chosen randomly, similar to a standard skip list.
+A node promoted to level $k$ has $k+1$ forward pointers (indexed 0 to $k$).
+The maximum number of levels in the skip list is a predefined constant, \texttt{MAX\_LEVEL}.
+The skip list employs a header node to initiate searches; its forward pointers are initially Nil.
+For simplicity in comparisons, the header node can be conceptually considered to hold a key value of negative infinity or have a special marker.
+Figure \ref{fig:insertion_example} illustrates an example of an insertion operation in SCSSL.
+%uncomment if require: \path (0,302); %set diagram left start at 0, and has height of 302
 
@@
   \includegraphics[width=\linewidth]{figures/skipinsert.jpg}
-\caption{insert 8 into simple cache-sentive skip list(max array size =2)}
-\label{fig:fig2}
+\caption{Insertion of key 8 into an SCSSL (max array size = 2). Key 8 displaces 9 from node (7,9). Key 9 is then inserted into a new node.}
+\label{fig:insertion_example}
 \end{figure}
@@
 \subsection{Initialization}
-The initialization operator is elementary, just create a header with MaxLevel forwards array, and set them to Nil. To simplify the algorithm, we set the header's array with a single value, -inf.
+The initialization process is elementary.
+A header node is created with an array of \texttt{MAX\_LEVEL+1} forward pointers, all initialized to Nil.
+To simplify comparisons, the header node's key array (if it were to have one in the same structure) can be considered to contain a single sentinel value of negative infinity, or it can be handled as a special case.
+In our algorithms, \texttt{header.FirstKey()} would effectively be $\infty$.
 
@@
 
-As the algorithm shows in Algorithm 1, from line 3 to line 5, it’s very similar to a standard skip list, but in line 4,current.forward[i].Key() returns the least value(at the first position) of the array in the current.forward[i].
+As the algorithm shows in Algorithm 1, from line 3 to line 5, it’s very similar to a standard skip list, but in line 4,current.forward[i].Key() returns the least value(at the first position) of the array in the \texttt{current.forward[i]}.
 Out of the while loop, the current’s forward Key() must be just greater than key, and if the key exists in the data structure, it must be in the current node array, so just search in the array of the current node in line 6.
@@
             $replace \gets current.array.pop()$\;
-            $current.insert\_into\_array(k)$\;
+            $current.insert\_into\_array(k)$\; \tcp{CASE 1}
             $k \gets replace$\;
@@
 
-        \If{$current \neq header \land \neg current.is\_full()$}{
+        \If{$current \neq header \land \neg current.is\_full()$}{ \tcp{CASE 2}
             $current.insert\_into\_array(k)$\;
         }
-        \Else{
+        \Else{ \tcp{CASE 3}
             $current \gets current.forward[0]$\;
@@
 
-\item CASE 1: current is not header, but current array size reach the maximum size(current.is\_full() function to check it) and key value is between the least element (first position, Key() return it) and the largest element(last position, current.array[-1]).
+\item CASE 1: current is not header, but current array size reach the maximum size(\texttt{current.is\_full()} function to check it) and key value is between the least element (first position, Key() return it) and the largest element(last position, \texttt{current.array[-1]}).
 So in this case, current node’s array is full, we make a small strick to deal with it, we pop the last position element, so the array is not full, and we insert the key in current node array(line 9,10) and it must be full again.then go on the next steps(for example, we replace 9 with 8 , and then insert 9 in another node, see Figure 2).
@@
 
-\item CASE 3: The key is lower than current.forward’s the least value of its array(ines 4-7 has insurance for this), and the key is greater than the largest element of current node’s array, So this key should be inserted into the current’s forward node.
+\item CASE 3: The key is lower than current.forward’s the least value of its array(lines 4-7 has insurance for this), and the key is greater than the largest element of current node’s array, So this key should be inserted into the current’s forward node.
 We just insert it when the node is not full (from line 15-18), and we do not pop last element like line 9-11, for just to be simple.
@@
 
-The deletion algorithm is shown in Algorithm 3, which should be noted that in line 5,  the condition checks whether the current forward array's largest element is less than k, so out of the while loop,  current.forward[0] is the first node whose largest element is equal to or greater than k, which means that if the key exists, it must be in the current node’s forward[0] array.
+The deletion algorithm is shown in Algorithm 3, which should be noted that in line 5,  the condition checks whether the current forward array's largest element is less than k, so out of the while loop,  \texttt{current.forward[0]} is the first node whose largest element is equal to or greater than k, which means that if the key exists, it must be in the current node’s \texttt{forward[0]} array.
 Line 8 to 14, delete the key in the selected array, and Line 15 to 21 checks whether the array is empty, if it is empty, we should delete the node from the data structure.
@@
 
-Here are the overall environments:
+The experiments were conducted in the following environments:
+\begin{itemize}
+    \item \textbf{Hardware 1 (MacBook):} Apple M2 CPU, 16 GB RAM.
+    \item \textbf{Hardware 2 (Server):} Intel(R) Core(TM) i7-6700 CPU @ 3.40GHz, 24 GB DDR4 2133 MHz RAM.
+This server was used not only for performance testing but also specifically for analyzing CPU cache miss rates using appropriate profiling tools (e.g.,  \texttt{perf} ).
+    \item \textbf{Compiler:} The algorithms were implemented in C++.
+The test programs were compiled using g++ (version specific to environment, e.g., 9.0 or higher) with the \texttt{-O3} optimization flag.
+    \item \textbf{Benchmark Configuration:}
+        Insertion operations in a skip list are prone to CPU cache misses due to dynamic memory allocations and pointer chasing.
+Therefore, our benchmarks primarily focus on insertion performance using randomly generated integer keys.
+The number of elements ranged from 100 to 300,000.
+        Search performance was also evaluated.
+However, we do not present detailed search results as the performance difference between SCSSL and the standard skip list was found to be negligible for typical search operations.
+This is likely because the dominant factor in search is the traversal of levels, which has a similar path length, and the final array scan in SCSSL is very fast for small arrays.
+        Both the standard skip list and SCSSL were configured with a maximum level (MAX\_LEVEL) of 16.
+For SCSSL, the maximum array size within a data node was set to a value empirically found to be effective (e.g., 64 or 128, chosen to fit well within L1 cache lines).
+\end{itemize}
 
-\textbf{Hardware}: We chose a MacBook whose CPU is Apple M2, and 16 GB of memory.
-and another server computer with Intel(R) Core(TM) i7-6700 CPU @ 3.40GHz , 24G ddr4 2133 memory.
-We use this server computer not only to test the performance, but also to test the CPU cache miss.
-
-\textbf{Compiler}: We complete the algorithm in cpp codes, The test program is compiled by g++ with O3 optimization option.
-
-\textbf{Benchmark}:  Because insert data in skip list, will more possibily cause CPU cache missing.
-so we test insertion with random data.
-and also give search test.
-The scale of data elements is from 100 to 300000.
-We do not present the search performance because the performance gap is negligible.
-
-\subsection{Performace}
+\subsection{Results and Discussion}
 \begin{figure}
@@
 
-We evaluated the standard skip list and SCSL with a maximum level of 16.
-Figure 3 presents the insertion performance comparison between the standard skip list and simple cache skip list in a Macbook.
-It shows that under small scale of data (< 1000) simple cache skip list can speed up to 1.28~1.39 times, and under medium scale (over 20000) , it can speed up to 1.55~1.65 times, as the scale increasing, the more benefit for performance.
-Figure 4 also shows that, in server computer, the simple cache skip list can speed up even 3 times.
 \begin{table*}[t]
@@
 \end{table*}
-As shown in the table above(table 1), the standard skip list in the test achieves a 33.22\% cache-miss rate, whereas SCSL has only a 0.89\% cache-miss rate.
-It also proves that adding arrays to data nodes can work very well.
+
+On the MacBook (Apple M2 processor, Figure 3 SCSSL demonstrates a speedup of 1.28x-1.39x for small datasets (<1,000 elements) during insertion.
+For medium-scale datasets (>20,000 elements), the speedup increases to a range of 1.55x-1.65x.
+This trend indicates that the cache-friendly benefits of SCSSL become more pronounced as the dataset size grows, leading to more memory accesses.
+
+On the server system (Intel i7-6700, Figure 4, SCSSL achieves even more significant speedups for insertions, reaching up to nearly 3x compared to the standard skip list for larger datasets (e.g., 300,000 elements).
+This enhanced improvement on the server platform might be attributed to differences in cache architecture, memory subsystem performance, or the relative cost of cache misses compared to the M2 architecture.
+
+Table 1 presents the cache performance data for inserting 300,000 random elements on the server.
+The standard skip list exhibits a high L1 data cache miss rate of 33.22\%.
+In contrast, SCSSL drastically reduces this rate to a mere 0.89\%.
+This substantial reduction in cache misses directly corroborates our hypothesis that embedding arrays within data nodes effectively improves data locality and cache utilization, which translates into the observed speedups.
+The significantly lower number of cache references for SCSSL also suggests more efficient data access patterns.
 
 \section{Conclusions}
-We present a new method to implement a cache-sensitive skip list, SCSL, which only changes a single element in the data-level nodes to an array.
-SCSL effectively leverages CPU caches by using data stored in continuous memory, and the algorithm is simple.
-Additionally, the performance results are also significant.
+
+We have presented SCSSL, a novel cache-sensitive skip list variant that introduces a simple yet highly effective modification: replacing single elements in data-level nodes with small, sorted arrays.
+This architectural change allows SCSSL to enhance CPU cache performance by improving data locality, while crucially maintaining the algorithmic simplicity that is a hallmark of skip lists.
+
+Experimental results demonstrate significant performance improvements for insertion operations, particularly on systems where cache performance is a critical factor.
+The observed speedups of 1.2x-3x, coupled with a dramatic reduction in cache miss rates (e.g., from 33.22\% to 0.89\% in our server tests), validate the efficacy of this approach.
+SCSSL offers a practical and easily implementable method to boost skip list performance in modern computing environments without resorting to complex algorithmic changes or specialized hardware features.
+Its simplicity makes it an attractive option for a wide range of applications, from embedded systems to large-scale in-memory data stores.
+
+Future work could explore optimal array sizes for different hardware platforms and key/value types, as well as investigate the application of SCSSL principles in concurrent skip list implementations.
+
 \begin{thebibliography}{9} 
